### 2019-08-21 manuscript/journal-applied-entomology/main.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A template for Wiley article submissions.
% Developed by Overleaf. 
%
% Please note that whilst this template provides a 
% preview of the typeset manuscript for submission, it 
% will not necessarily be the final publication layout.
%
% Usage notes:
% The "blind" option will make anonymous all author, affiliation, correspondence and funding information.
% Use "num-refs" option for numerical citation and references style.
% Use "alpha-refs" option for author-year citation and references style.

\documentclass[alpha-refs]{wiley-article}
% \documentclass[blind,num-refs]{wiley-article}

% Add additional packages here if required
\usepackage{siunitx}
\usepackage{lineno}

% Update article type if known
\papertype{Original Article}
% Include section in journal if known, otherwise delete
\paperfield{Pest Management Science}

\title{Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping}

% List abbreviations here, if any. Please note that it is preferred that abbreviations be defined at the first instance they appear in the text, rather than creating an abbreviations list.
%\abbrevs{ABC, a black cat; DEF, doesn't ever fret; GHI, goes home immediately.}

% Include full author names and degrees, when required by the journal.
% Use the \authfn to add symbols for additional footnotes and present addresses, if any. Usually start with 1 for notes about author contributions; then continuing with 2 etc if any author has a different present address.
\author[1\authfn{1}]{Denis S. Willett}
\author[1\authfn{1}]{Camila C. Filgueiras}
\author[2]{Starker Wright}
\author[1]{Jan P. Nyrop}
\author[1]{Brian A. Nault}

\contrib[\authfn{1}]{Equally contributing authors.}

% Include full affiliation details for all authors
\affil[1]{Department of Entomology, Cornell AgriTech, Cornell University, Geneva, NY, 14456, USA}
\affil[2]{Bartlett Tree Experts, Dublin, PA, USA}

\corraddress{Denis S. Willett, 15 Castle Creek Drive, Geneva, NY 14456}
\corremail{deniswillett@cornell.edu}

% Include the name of the author that should appear in the running header
\runningauthor{Willett et al.}

\begin{document}

\maketitle

\begin{abstract}
Onion maggot (\textit{Delia antiqua}) is an economically important pest of alliums in temperate regions throughout the world.  Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.  Both means of control rely upon effective monitoring of \textit{D. antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of adult onion maggot flies to accurately reflect population dynamics.  We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.  White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.  These results suggest an improved means of monitoring onion maggot populations which will be useful in informing modeling and monitoring efforts especially in areas where onion maggot is an emergent pest.

% Please include a maximum of seven keywords
\keywords{Onion Maggot, \textit{Delia antiqua}, attraction, sticky-trap, attract-and-kill, lure, onion management}
\end{abstract}

\linenumbers
\section{Introduction}

The onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops worldwide.  Found primarily in temperate climates, \textit{D. antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on Onions (\textit{Allium cepa} L.), Garlic (\textit{Allium sativem} L.), Scallions (\textit{Allium fistulosum} L.), and Chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.  Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where resistant populations have developed \citep{martinson1988dispersal, nault2006onion}.

Onion maggot is a primary pest in part due to its lifecycle.  It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.  Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.  First generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.  In addition, damaged plants become more susceptible to infestation by subsequent generations, pathogens, and damage at harvest time \citep{eckenrode1986impact,nault2006performance}.  Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.

Management of this pest has relied on in-furrow insecticide application at planting \citep{nault2006performance}.  A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.  Chlorpyrifos is commonly used as a drench treatment currently in combination with a Cyromazine seed treatment \citep{nault2006performance}.  Fipronil and Spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to Chlorpyrifos \citep{nault2006onion}.  Cultural practices such as rotation, removal of damaged onions, and delayed planting remain effective management alternatives \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.

Delayed planting can be an effective control tactic because onion development if offset phenologically from development of onion maggot oviposition and larval development \citep{nault2011delaying}.  Such tactics, and effective control in general, rely on monitoring onion maggot populations in the field.  While useful in areas where onion maggot populations are already established, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.

Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principle methods: sticky traps, water traps, and simulation.  Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.  Trap catch of adult onion maggot flies can be low compared to field populations.  Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.  Odor sources of attractants have also been added to traps in an effort to make them more attractive, but with limited success.  Simulation has relied on field data from traps, phenological studies in the lab, and climate information \citep{thomingdeveloping,otto2000development,ning2017predicting}.  Population simulations can prove useful at larger scales, but often lack extremely detailed location specific information necessary for producers to determine if they have a severe problem in a specific field.

To further develop effective monitoring methodologies for the onion maggot, we evaluated a number of factors likely to influence attraction of adult onion maggot flies.  Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}. We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate monitoring potential and efficacy.

\section{Materials and Methods}

To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.  Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (\textbf{Company Info here - is this ChemTica?}) attractant to evaluate potential improvement in trap catch.

All shape, size, and color trials were conducted in commercial dry bulb onion fields on muck soil near Elba, NY in western upstate New York. Muck soils are high-organic matter soils formed from old lake beds.  Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.  All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.  No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.  This management is unlikely to affect \textit{D. antiqua} populations due to spray timing and minimal impacts of thrips sprays on onion maggot fly \citep{finch1986behavior}.

\subsection{Field Trials}

\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.  Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.  Traps were placed in the field in late May then collected in late June.

\paragraph{Size Trial}
To evaluate the influence of trap size on the trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm diameter were placed along the long edge of onion fields with spacing 15.24 meters apart in a randomized controlled block design with five replications.

\paragraph{Color Trial}
To evaluate the effect of color on trap catch and monitoring of adult onion maggot fly, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.

\paragraph{Delia Lure Trial}
To evaluate the effect of adding an attractant an trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).  Trap Catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.

\subsection{Analysis}

Raw data from shape, size, and color trials were analyzed using linear models and analysis of variance.  Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations. Based on these considerations, an outlier was detected and removed from the shape trials (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.

Raw data from the Delia Lure Trial were analyzed with a paired t-test due to the nature of the experimental design.  Conformation to assumptions of normality were confirmed through examination of quantile-quantile plots.

\subsection{Data Management}

All data for the trials were entered into flat tabular (.csv) files.  All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.  The $tidyverse$, $car$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, emmeans}.  All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction).

\section{Results}

\paragraph{Shape Trial} Models relating trap shape and \textit{D. antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (P \textless 0.001, $R^2_{adj}$ = 0.70, Table \ref{table:1}).  Trap shape significantly influenced (P = 0.005) catch of adult \textit{D. antiqua} (Figure \ref{fig:figure1}).  Sticky traps caught approximately 27.81 $\pm$ 2.8 more female flies than male flies.  Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.  While there were no significant differences between females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.  No significant differences were observed between male trap catch.

\begin{table}[]
\caption{Linear model and analysis of variance results and diagnostics for shape, size, and color trials.  Treatment refers to the factor under evaluation. For the shape trial, treatment denotes shape; for the size trial, treatment denotes size; for the color trial, treatment denotes color.  Missing values indicate that factor was not included in the best fit model.  All code and additional documentation is available on GitHub.  }
\begin{tabular}{lrrrrrrrrr}
              & \multicolumn{9}{c}{Trial}                                                                                                                                                                                                \\ \cline{2-10} 
              & \multicolumn{3}{c}{Shape}                                              & \multicolumn{3}{c}{Size}                                               & \multicolumn{3}{c}{Color}                                              \\
              & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} \\ \cline{2-10}
Sex           & 42                    & 1                      & \textless 0.0001      & 197.5                 & 1                      & \textless 0.0001      & 37.2                  & 1                      & \textless 0.0001      \\
Treatment     & 4.4                   & 4                      & 0.005                 & 11.6                  & 4                      & \textless 0.0001      & 31.3                  & 3                      & \textless 0.0001      \\
Year          &                       &                        &                       & 142.4                 & 1                      & \textless 0.0001      &                       &                        &                       \\
Sex:Treatment &                       &                        &                       &                       &                        &                       & 6.3                   & 3                      & 0.002                 \\
Sex:Year      &                       &                        &                       & 137.9                 & 1                      & \textless 0.0001      &                       &                        &                       \\ \cline{2-10} 
              &                       &                        &                       &                       &                        &                       &                       &                        &                       \\
$R^2$            &                       &                        & 0.75                  &                       &                        & 0.75                  &                       &                        & 0.83                  \\
$R^2_{adj}$         &                       &                        & 0.70                  &                       &                        & 0.73                  &                       &                        & 0.79                  \\
P             &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001     
\end{tabular}
\label{table:1}
\end{table}

\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).  Trap size significantly influenced trap catch (P \textless 0.001).  Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.  While male trap catch was less than that of females, trends in catch amoung the different diameters were similar for both males and females.

\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.79, Table \ref{table:1}). Color significantly influenced trap catch (P \textless 0.001) with white traps catching significantly more females than any other color (t \textless -3.1, df = 32, P \textless 0.012) and significantly more males than any other color except yellow (t \textless -3.1, df = 32, P \textless 0.012, Yellow: t = -1.6, df = 32, P = 0.3).  White traps caught significantly more females than males (t = 6.1, df = 32, P \textless 0.001).

\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.  Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
\caption{Adult onion maggot fly catch on sticky traps of different shape.  Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.  Letters not shared between groups denote significant differences in female trap catch (there was no observed difference in male trap catch) at $\alpha$ = 0.05 with Tukey's HSD test. }
\label{fig:figure1}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
\caption{Adult onion maggot fly catch on spherical sticky traps of different size.  Points and error bars denote mean and 95\% confidence intervals respectively.  Letters not shared between groups indicates significant differences in adult catch at $\alpha$ = 0.05 with Tukey's HSD test.}
\label{fig:figure2}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
\caption{Adult onion maggot fly catch on spherical sticky traps of different color.  Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.  \textbf{*} indicates significantly different trap catch on white sticky traps (P = 0.012).}
\label{fig:figure3}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
\caption{Adult onion maggot fly catch on sticky traps baited with Delia Lure attractant and unbaited.  Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.  \textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030). }
\label{fig:figure4}
\end{figure}

\section{Discussion}

Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of adult onion maggot flies.  Short cylinder traps performed better than most other shapes and were not significantly different from spherical traps.  Spherical traps were more economical to produce and use so they were selected for use in subsequent studies.  Size played a large role in increasing trap catch.  Larger diameter traps with more surface area captured more adult onion maggot flies.  Color had perhaps the largest impact on catch of adult onion maggot flies with white traps far outperforming yellow, green and red traps.

The combination of sticky traps with the attractive Delia Lure also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.  Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.

Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching onion maggot adults \citep{thomingdeveloping}.  This work showed that white traps far outperform sticky traps of other colors confirming findings in another study that white traps work well for \textit{Delia} flies.  Interestingly, other work has suggested that specificity for \textit{D. antiqua} could be improved with the color blue, but that overal trap catch may suffer \citep{thomingdeveloping}.

These results suggest a way forward in improving monitoring ability of onion maggot fly adults in the field.  A spherical, white, large diameter stick trap baited with Delia Lure is the best option for monitoring adult onion maggot flies out of the various factors tested in these trials.  Accurate monitoring of onion maggot populations better informs producers about pest management challenges, especially in areas where onion maggot is an emergent pest.  Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \cite{ning2017predicting, otto2000development,thomingdeveloping}.

The ability to attract larger numbers of adult onion maggot flies also opens the possibility for a different, more environmentally friendly, management method.  If larger number of flies can be attracted then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be controlled.  'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.  Using large, white, spherical traps in conjunction with Delia Lure may provide the attraction needed to make it possible to control these pests using attract and kill strategies.

\section*{Acknowledgements}
Suggestions for acknowledgements?

\section*{Conflict of Interest}
The authors declare no conflict of interest.

\section*{Author Contribution}
BAN, JPN, and SW designed the experiments.  DSW, CCF, and BAN analyzed the data and wrote the manuscript.

\section*{Data Availability Statement}
All code and data, including manuscript documentation, is available on GitHub(https://github.com/acetworld/onion-maggot-attraction).

%\printendnotes

% Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.

\section{References}

\bibliographystyle{vancouver-authoryear}
\bibliography{om-attraction}

\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}

\end{document}

### 2019-08-21 analysis/appl_ent_figure_theme.R

@@ -1,0 +1,22 @@
+############################
+#                          #
+#       Figure Theme       #
+#                          #
+############################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+applied_entomology_theme <- theme_bw() +
+    theme(legend.background = element_rect(color = 'grey30'),
+          panel.border = element_blank(),
+          panel.grid = element_blank(),
+          axis.line.x = element_line(size = 0.48, linetype = 'solid', 
+                                     color = 'black'),
+          axis.line.y = element_line(size = 0.48, linetype = 'solid', 
+                                     color = 'black'),
+          legend.margin = ggplot2::margin(1.24, 1.24, 1.24, 1.24),
+          legend.title = element_blank(),
+          legend.position = c(0.75, 0.75)
+          )

### 2019-08-21 analysis/model_diagnostics.R

@@ -1,0 +1,34 @@
+################################################
+#                                              #
+#       Model Diagnostic Helper Function       #
+#                                              #
+################################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+model_diagnostics <- function(linear_model, to_plot = TRUE) {
+    print('Model Summary')
+    print('------------------')
+    print(summary(linear_model))
+    print('')
+    
+    print('ANOVA')
+    print('------------------')
+    print(car::Anova(linear_model, type = 'III'))
+    print('')
+    
+    
+    print('Information Criteria')
+    print('------------------')
+    print('AIC')
+    print(AIC(linear_model))
+    print('BIC')
+    print(BIC(linear_model))
+    
+    if(to_plot) {
+        car::qqPlot(linear_model, type = 'III')
+        plot(linear_model, which = 1:6)
+    }
+}

### 2019-08-21 analysis/om_color_trials_2005.R

@@ -1,0 +1,95 @@
+#########################################
+#                                       #
+#       Onion Maggot Color Trials       #
+#                                       #
+#########################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+source('./analysis/appl_ent_figure_theme.R')
+
+
+# Dato Processing ----------------------------
+
+# Load data for color trial
+color_trials <- read_csv('./data/om_color_trials_2005.csv', skip = 19)
+
+# Information on treatments documented in csv file
+treatment_info <- tibble(
+    treatment = c(8, 10,11,12),
+    color = factor(c('White',
+              'Yellow',
+              'Green',
+              'Red'),
+              levels = c('White',
+                         'Yellow',
+                         'Green',
+                         'Red'))
+)
+
+# Reshape the data and join with treatment information
+color_trial_treatment <- color_trials %>% 
+    gather(sex, flies, males, females) %>%
+    left_join(treatment_info)
+
+# Modeling --------------------------
+
+# Linear model relating sex and color to fly catch
+color_mod <- lm(flies ~ sex * color, data = color_trial_treatment)
+
+# Print and plot model diagnostics
+# model_diagnostics(color_mod) # Run to see plots
+model_diagnostics(color_mod, to_plot = FALSE)
+
+# Non-normality and slight heteroscedascity detected
+# Square root transform applied
+color_mod_transform <- lm(sqrt(flies) ~ sex * color, data = color_trial_treatment)
+
+# Model diagnostics of new model - resolved issues
+# model_diagnostics(color_mod_transform) # Run to see plots
+model_diagnostics(color_mod_transform, to_plot = FALSE)
+
+# Contrasts and post-hoc tests
+emmeans(color_mod_transform, ~ sex * color, type = 'response') %>% 
+    contrast(method = 'dunnett', by = 'sex')
+
+emmeans(color_mod_transform, ~sex * color, type = 'response') %>%
+    contrast(method = 'tukey', by = 'color')
+
+# Figure generation -----------------------------
+
+# Set plotting parameters
+dodge_width = 0.48
+jitter_width = 0.12
+
+# Set seed for reproducibility
+set.seed(72)
+
+# generate figure
[…]

### 2019-08-21 analysis/om_delia_lure_2006.R

@@ -1,0 +1,60 @@
+##############################################
+#                                            #
+#       Onion Maggot Delia Lure Trials       #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+source('./analysis/appl_ent_figure_theme.R')
+
+
+# Dato Processing ----------------------------
+
+# Load data for color trial
+delia_lure_trial <- read_csv('./data/om_delia_lure_2006.csv', skip = 9) %>% 
+    # reported numbers are total counts for four sticky cards divided by four.
+    # we'll multiply by 4 to bring back to total counts.
+    mutate(total_onion_maggot = as.integer(onion_maggot * 4)) %>% 
+    select(-onion_maggot)
+
+# Reformat for t-test
+prep_ttest <- delia_lure_trial %>% spread(treatment, total_onion_maggot)
+
+# Modeling --------------------------
+
+# Paired t-test by location and day
+t.test(prep_ttest$Baited, prep_ttest$Unbaited, paired = TRUE)
+
+# Check for normality
+qqPlot(delia_lure_trial$total_onion_maggot)
+
+# Figure generation -----------------------------
+
+# Set seed for reproducibility
+set.seed(24)
+
+# Generate figure
+delia_lure_figure <- ggplot(delia_lure_trial, aes(x = treatment, y = total_onion_maggot)) + 
+    stat_summary(fun.data = 'mean_cl_boot', 
+                 geom = 'errorbar',
+                 width = 0.24) +
+    stat_summary(fun.data = 'mean_cl_boot',
+                 geom = 'point') + 
+    geom_point(position = position_jitter(0.12),
+               alpha = 0.48) + 
+    labs(x = 'Treatment', y = 'Total Onion Maggot Fly Adults') +
+    applied_entomology_theme
+
+# Save figure
+ggsave(plot = delia_lure_figure,
+       filename = './figures/raw/delia_lure_figure.pdf',
+       width = 4, height = 3)

### 2019-08-21 analysis/om_shape_trials_2005.R

@@ -1,0 +1,109 @@
+##############################################
+#                                            #
+#       Onion Maggot Shape Trials            #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+source('./analysis/appl_ent_figure_theme.R')
+
+
+# Dato Processing ----------------------------
+
+# Load data for shape trial
+shape_trial_results <- read_csv('./data/om_shape_trials_2005.csv', skip = 17)
+
+# Shape treatment info from csv file
+treatment_info <- tibble(
+    treatment = 1:5,
+    treatment_shape = factor(c('Short Cylinder',
+                        'Tall Cylinder',
+                        'Cube',
+                        'Square Panel',
+                        'Sphere'
+                        ),
+                        levels = c('Short Cylinder',
+                                   'Sphere',
+                                   'Cube',
+                                   'Square Panel',
+                                   'Tall Cylinder'
+                        ))
+)
+
+# Reshape the data and join with treatment information
+shape_trial <- shape_trial_results %>% 
+    gather(key = sex, value = flies, -treatment, -replication) %>% 
+    left_join(treatment_info)
+
+
+# Modeling --------------------------
+
+# Linear model relating sex and color to fly catch
+shape_mod <- lm(flies ~ sex * treatment_shape, data = shape_trial)
+
+# Print and plot model diagnostics
+# model_diagnostics(shape_mod) # Run to see plots
+model_diagnostics(shape_mod, to_plot = FALSE)
+
+# Based on diagnostics, there seems to be an outlier
+outlierTest(shape_mod) # check outlier
+
+# Remodel with outlier removed
+shape_mod_xoutlier <- lm(flies ~ sex * treatment_shape, data = shape_trial[-31,])
+
+# Print and plot model diagnostics
+# model_diagnostics(shape_mod_xoutlier) # Run to see plots
+model_diagnostics(shape_mod_xoutlier, to_plot = FALSE)
+
+# Contrasts and post-hoc tests
+emmeans(shape_mod_xoutlier, ~sex ) %>% contrast(method = 'tukey')
+
[…]

### 2019-08-21 analysis/om_size_trials.R

@@ -1,0 +1,110 @@
+#########################################
+#                                       #
+#       Onion Maggot Size Trials       #
+#                                       #
+#########################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+source('./analysis/appl_ent_figure_theme.R')
+
+
+# Dato Processing ----------------------------
+
+# Load data for 2005 size trial
+size_trial_2005 <- read_csv('./data/om_size_trials_2005.csv', 
+                            skip = 25)
+
+# Information on treatments documented in csv file
+treatment_info_2005 <- tibble(
+    treatment = 5:9,
+    #size is diameter of sphere in centimeters
+    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
+                  levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
+)
+
+# Reformat 2005 data, add in treatment and year information
+size_trial_treatment_2005 <- size_trial_2005 %>% 
+    gather(sex, flies, males, females) %>% 
+    left_join(treatment_info_2005) %>% 
+    mutate(year = '2005') %>% 
+    select(sex, size, flies, year)
+
+
+# Load data for 2006 size trial
+size_trial_2006 <- read_csv('./data/om_size_trials_2006.csv', 
+                            skip = 16, col_types = c('ccccii'))
+
+# Information on treatments documented in csv file
+treatment_info_2006 <-tibble(
+    treatment = as.character(6:10),
+    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
+                  levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
+    )
+
+# Reformat 2006 data, add in treatment and year information
+size_trial_treatment_2006 <- size_trial_2006 %>% 
+    select(-size) %>% 
+    gather(sex, flies, females, males) %>% 
+    left_join(treatment_info_2006) %>%
+    mutate(year = '2006') %>% 
+    select(sex, size, flies, year)
+
+# Combine years
+size_trial <- bind_rows(size_trial_treatment_2006, size_trial_treatment_2005)
+
+# Modeling --------------------------
+
+# Linear model relating sex and color to fly catch
[…]

### 2019-08-21 analysis/om_size_trials_2005.R

@@ -1,0 +1,55 @@
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+
+
+size_trial <- read_csv('./data/om_size_trials_2005.csv', 
+                       skip = 25)
+
+treatment_info <- tibble(
+    treatment = 5:9,
+    #size is diameter of sphere in centimeters
+    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
+                         levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
+)
+
+size_trial_treatment <- size_trial %>% 
+    gather(sex, flies, males, females) %>% 
+    left_join(treatment_info)
+
+size_mod <- lm(flies ~ sex * size, data = size_trial_treatment)
+
+model_diagnostics(size_mod)
+
+emmeans(size_mod, ~ sex * size) %>% contrast(by = 'sex', method = 'dunnett')
+emmeans(size_mod, ~ sex * size) %>% contrast(simple = 'sex', method = 'tukey')
+emmeans(size_mod, ~ sex * size) %>% cld(details = TRUE)
+
+stat_labels <- emmeans(size_mod, ~ sex * size) %>% 
+    cld() %>% data.frame() %>% 
+    filter(sex == 'females') %>% 
+    mutate(label = c('B', 'B', 'AB', 'AB', 'A'))
+
+dodge_width = 0.48
+jitter_width = 0.12
+ggplot(size_trial_treatment, aes(x = size, y = flies, color = sex)) + 
+    stat_summary(fun.data = 'mean_cl_boot', 
+                 geom = 'errorbar',
+                 position = position_dodge(dodge_width),
+                 width = dodge_width/2) +
+    stat_summary(fun.data = 'mean_cl_boot',
+                 geom = 'point',
+                 position = position_dodge(dodge_width)) +
+    geom_point(position = position_jitterdodge(dodge.width = dodge_width,
+                                               jitter.width = jitter_width),
+               alpha = 0.48) + 
+    geom_text(data = stat_labels, 
+              aes(x = size, y= 72, label = label),
+              show.legend = FALSE) + 
+    scale_color_grey() + 
+    theme_bw() + 
+    labs(x = 'Sphere Trap Diameter (cm)', y = 'Onion Maggot Fly Adults') + 
+    theme(legend.title = element_blank(),
+          legend.position = c(0.75, 0.75),
+          legend.background = element_rect(color = 'grey30'))

### 2019-08-21 manuscript/pest-management-science/main.tex
added data and analysis files

--- 2019-08-21 manuscript/journal-applied-entomology/main.tex
@@
 
-\title{Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping}
+\title{title}
 
@@
 \begin{abstract}
-Onion maggot (\textit{Delia antiqua}) is an economically important pest of alliums in temperate regions throughout the world.
-Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.
-Both means of control rely upon effective monitoring of \textit{D.
-antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of adult onion maggot flies to accurately reflect population dynamics.
-We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.
-White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.
-These results suggest an improved means of monitoring onion maggot populations which will be useful in informing modeling and monitoring efforts especially in areas where onion maggot is an emergent pest.
 
@@
 \section{Introduction}
-
-The onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops worldwide.
-Found primarily in temperate climates, \textit{D.
-antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on Onions (\textit{Allium cepa} L.), Garlic (\textit{Allium sativem} L.), Scallions (\textit{Allium fistulosum} L.), and Chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
-Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where resistant populations have developed \citep{martinson1988dispersal, nault2006onion}.
-
-Onion maggot is a primary pest in part due to its lifecycle.
-It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.
-Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.
-First generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
-In addition, damaged plants become more susceptible to infestation by subsequent generations, pathogens, and damage at harvest time \citep{eckenrode1986impact,nault2006performance}.
-Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.
-
-Management of this pest has relied on in-furrow insecticide application at planting \citep{nault2006performance}.
-A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
-Chlorpyrifos is commonly used as a drench treatment currently in combination with a Cyromazine seed treatment \citep{nault2006performance}.
-Fipronil and Spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to Chlorpyrifos \citep{nault2006onion}.
-Cultural practices such as rotation, removal of damaged onions, and delayed planting remain effective management alternatives \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
-
-Delayed planting can be an effective control tactic because onion development if offset phenologically from development of onion maggot oviposition and larval development \citep{nault2011delaying}.
-Such tactics, and effective control in general, rely on monitoring onion maggot populations in the field.
-While useful in areas where onion maggot populations are already established, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
-
-Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principle methods: sticky traps, water traps, and simulation.
-Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
-Trap catch of adult onion maggot flies can be low compared to field populations.
-Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
-Odor sources of attractants have also been added to traps in an effort to make them more attractive, but with limited success.
-Simulation has relied on field data from traps, phenological studies in the lab, and climate information \citep{thomingdeveloping,otto2000development,ning2017predicting}.
-Population simulations can prove useful at larger scales, but often lack extremely detailed location specific information necessary for producers to determine if they have a severe problem in a specific field.
-
-To further develop effective monitoring methodologies for the onion maggot, we evaluated a number of factors likely to influence attraction of adult onion maggot flies.
-Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
-We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate monitoring potential and efficacy.
-
 \section{Materials and Methods}
-
-To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
-Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (\textbf{Company Info here - is this ChemTica?}) attractant to evaluate potential improvement in trap catch.
-
-All shape, size, and color trials were conducted in commercial dry bulb onion fields on muck soil near Elba, NY in western upstate New York.
-Muck soils are high-organic matter soils formed from old lake beds.
-Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.
-All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.
-No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.
-This management is unlikely to affect \textit{D.
-antiqua} populations due to spray timing and minimal impacts of thrips sprays on onion maggot fly \citep{finch1986behavior}.
 
@@
 \subsection{Analysis}
-
-Raw data from shape, size, and color trials were analyzed using linear models and analysis of variance.
-Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
-Based on these considerations, an outlier was detected and removed from the shape trials (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.
-
-Raw data from the Delia Lure Trial were analyzed with a paired t-test due to the nature of the experimental design.
-Conformation to assumptions of normality were confirmed through examination of quantile-quantile plots.
-
 \subsection{Data Management}
-
-All data for the trials were entered into flat tabular (.csv) files.
-All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.
-The $tidyverse$, $car$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, emmeans}.
-All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction).
 
@@
 No significant differences were observed between male trap catch.
-
-\begin{table}[]
-\caption{Linear model and analysis of variance results and diagnostics for shape, size, and color trials.
-Treatment refers to the factor under evaluation.
-For the shape trial, treatment denotes shape; for the size trial, treatment denotes size; for the color trial, treatment denotes color.
-Missing values indicate that factor was not included in the best fit model.
-All code and additional documentation is available on GitHub.
-}
-\begin{tabular}{lrrrrrrrrr}
-              & \multicolumn{9}{c}{Trial}                                                                                                                                                                                                \\ \cline{2-10}
-              & \multicolumn{3}{c}{Shape}                                              & \multicolumn{3}{c}{Size}                                               & \multicolumn{3}{c}{Color}                                              \\
-              & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} \\ \cline{2-10}
-Sex           & 42                    & 1                      & \textless 0.0001      & 197.5                 & 1                      & \textless 0.0001      & 37.2                  & 1                      & \textless 0.0001      \\
-Treatment     & 4.4                   & 4                      & 0.005                 & 11.6                  & 4                      & \textless 0.0001      & 31.3                  & 3                      & \textless 0.0001      \\
-Year          &                       &                        &                       & 142.4                 & 1                      & \textless 0.0001      &                       &                        &                       \\
-Sex:Treatment &                       &                        &                       &                       &                        &                       & 6.3                   & 3                      & 0.002                 \\
-Sex:Year      &                       &                        &                       & 137.9                 & 1                      & \textless 0.0001      &                       &                        &                       \\ \cline{2-10}
-              &                       &                        &                       &                       &                        &                       &                       &                        &                       \\
-$R^2$            &                       &                        & 0.75                  &                       &                        & 0.75                  &                       &                        & 0.83                  \\
-$R^2_{adj}$         &                       &                        & 0.70                  &                       &                        & 0.73                  &                       &                        & 0.79                  \\
-P             &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001
-\end{tabular}
-\label{table:1}
-\end{table}
 
@@
 
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
-\caption{Adult onion maggot fly catch on sticky traps of different shape.
-Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.
-Letters not shared between groups denote significant differences in female trap catch (there was no observed difference in male trap catch) at $\alpha$ = 0.05 with Tukey's HSD test.
-}
-\label{fig:figure1}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
-\caption{Adult onion maggot fly catch on spherical sticky traps of different size.
-Points and error bars denote mean and 95\% confidence intervals respectively.
-Letters not shared between groups indicates significant differences in adult catch at $\alpha$ = 0.05 with Tukey's HSD test.}
-\label{fig:figure2}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
-\caption{Adult onion maggot fly catch on spherical sticky traps of different color.
-Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
-\textbf{*} indicates significantly different trap catch on white sticky traps (P = 0.012).}
-\label{fig:figure3}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
-\caption{Adult onion maggot fly catch on sticky traps baited with Delia Lure attractant and unbaited.
-Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
-\textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030).
-}
-\label{fig:figure4}
-\end{figure}
-
 \section{Discussion}
-
-Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of adult onion maggot flies.
-Short cylinder traps performed better than most other shapes and were not significantly different from spherical traps.
-Spherical traps were more economical to produce and use so they were selected for use in subsequent studies.
-Size played a large role in increasing trap catch.
-Larger diameter traps with more surface area captured more adult onion maggot flies.
-Color had perhaps the largest impact on catch of adult onion maggot flies with white traps far outperforming yellow, green and red traps.
-
-The combination of sticky traps with the attractive Delia Lure also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
-Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.
-
-Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching onion maggot adults \citep{thomingdeveloping}.
-This work showed that white traps far outperform sticky traps of other colors confirming findings in another study that white traps work well for \textit{Delia} flies.
-Interestingly, other work has suggested that specificity for \textit{D.
-antiqua} could be improved with the color blue, but that overal trap catch may suffer \citep{thomingdeveloping}.
-
-These results suggest a way forward in improving monitoring ability of onion maggot fly adults in the field.
-A spherical, white, large diameter stick trap baited with Delia Lure is the best option for monitoring adult onion maggot flies out of the various factors tested in these trials.
-Accurate monitoring of onion maggot populations better informs producers about pest management challenges, especially in areas where onion maggot is an emergent pest.
-Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \cite{ning2017predicting, otto2000development,thomingdeveloping}.
-
-The ability to attract larger numbers of adult onion maggot flies also opens the possibility for a different, more environmentally friendly, management method.
-If larger number of flies can be attracted then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be controlled.
-'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
-Using large, white, spherical traps in conjunction with Delia Lure may provide the attraction needed to make it possible to control these pests using attract and kill strategies.
 
@@
 
-% Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
-
 \section{References}

### 2019-08-21 analysis/model_diagnostics.R

@@ -27,8 +27,14 @@ model_diagnostics <- function(linear_model, to_plot = TRUE) {
     print('BIC')
     print(BIC(linear_model))
     
+    print('Non-constant Variance Score Test')
+    print('------------------')
+    print(car::ncvTest(linear_model))
+    print('')
+    
     if(to_plot) {
         car::qqPlot(linear_model, type = 'III')
+        car::crPlots(linear_model)
         plot(linear_model, which = 1:6)
     }
 }

### 2019-08-21 analysis/om-spinosad-field-damage_2007.R

@@ -1,0 +1,183 @@
+##############################################
+#                                            #
+#       Onion Maggot Spinosad                #
+#        Field OM Damage 2007                #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+library(tidyverse)
+library(car)
+library(emmeans)
+library(lme4)
+source('./analysis/model_diagnostics.R')
+source('./analysis/pest_management_science_theme.R')
+
+
+# Load data -----------
+
+field_damage <- read_csv('./data/om-spinosad-field-damage-trial-2007.csv', skip = 17)
+
+# Preprocess data ------------------
+
+# Treatment information
+control_treatment <- tibble(
+    treatment = 1:6,
+    control_type = c('Insecticide',
+                     'No Insecticide',
+                     'Sticky Card',
+                     'Sticky Card',
+                     'Spinosad Sphere',
+                     'Spinosad Sphere')
+)
+
+# Look at field damage over time 
+field_damage_time <- field_damage %>% 
+    gather(key = 'info', value = 'damage', contains('dam')) %>%
+    mutate(month = str_sub(info, 4,4),
+           day = str_sub(info, 5),
+           date = lubridate::mdy(paste(month, day, '2007')),
+           delia_lure = if_else(treatment %in% c(4,6), 'Lure','No Lure')) %>%
+    left_join(control_treatment) %>%
+    arrange(treatment, replication, date) %>% 
+    group_by(treatment, replication) %>% 
+    mutate(cumulative = cumsum(damage),
+           cumulative_adj = cumulative/initstnd,
+           date = as.factor(date))
+
+# Pull out end of season stand numbers
+stand_numbers <- field_damage_time %>% 
+    group_by(treatment, delia_lure, control_type, replication) %>%
+    summarize(starting_stand = first(initstnd),
+              ending_stand = first(finlst)) %>%
+    mutate(loss = starting_stand - ending_stand)
+
+# Model Stand Loss -----------------------
+
+# Basic model for stand loss
+stand_loss_mod <- lm(loss ~ control_type, 
+                     data = stand_numbers)
+model_diagnostics(stand_loss_mod, to_plot = FALSE)
+outlierTest(stand_loss_mod) # Marginal outlier... leave in
+
[…]

### 2019-08-21 analysis/om-spinosad-field-damage_2008.R

@@ -1,0 +1,91 @@
+##############################################
+#                                            #
+#       Onion Maggot Spinosad                #
+#        Field OM Damage 2008                #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+library(tidyverse)
+library(car)
+library(emmeans)
+library(lme4)
+source('./analysis/model_diagnostics.R')
+source('./analysis/pest_management_science_theme.R')
+
+
+# Load data -----------
+
+field_damage <- read_csv('./data/om-spinosad-field-damage-trial-2008.csv', skip = 17)
+
+# Preprocess data ------------------
+
+# Treatment information
+control_treatment <- tibble(
+    treatment = 1:3,
+    control_type = c('No Insecticide',
+                     'Spinosad',
+                     'Spinosad +')
+)
+
+# Look at field damage over time 
+field_damage_time <- field_damage %>% 
+    gather(key = 'info', value = 'damage', contains('dam')) %>%
+    mutate(month = str_sub(info, 4,4),
+           day = str_sub(info, 5),
+           date = lubridate::mdy(paste(month, day, '2008'))) %>%
+    left_join(control_treatment) %>%
+    arrange(control_type, replication, date) %>% 
+    group_by(control_type, replication) %>% 
+    mutate(cumulative = cumsum(damage),
+           date = as.factor(date))
+
+# Model cumulative damage -------------------
+
+# Null model for comparison
+null_damage_mod <- lmer(cumulative ~ 1 + (1 | date),
+                        data = field_damage_time)
+
+# Fixed effects for comparison
+fixed_damage_mod <- lm(cumulative ~ control_type,
+                         data = field_damage_time)
+
+# Full model evaluating treatment
+field_damage_mod <- lmer(cumulative ~ control_type + 
+                             (1 |date), 
+                         data = field_damage_time)
+
+# Examine models
+plot(field_damage_mod)
+summary(field_damage_mod)
+anova(null_damage_mod, fixed_damage_mod, field_damage_mod)
+Anova(field_damage_mod)
+rcompanion::nagelkerke(field_damage_mod, null_damage_mod)
+rmse <- resid(field_damage_mod)^2 %>% mean() %>% sqrt()
[…]

### 2019-08-21 analysis/om-spinosad-field-time-dose.R

@@ -1,0 +1,55 @@
+##############################################
+#                                            #
+#       Onion Maggot Spinosad                #
+#           Field OM Catch                   #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+library(tidyverse)
+library(car)
+library(emmeans)
+source('./analysis/model_diagnostics.R')
+source('./analysis/pest_management_science_theme.R')
+
+# Load Data ------------------
+field_trap_catch <- read_csv('./data/om-spinosad-field-time-dose-trial-2006.csv', skip = 8)
+
+# Preprocess Data --------------------
+
+# Reorganize data for plotting
+daily_trap_catch <- field_trap_catch %>% 
+    gather(key = 'info', value = 'catch', -replication) %>% 
+    mutate(sex = if_else(str_sub(info, 1, 3) == 'fem',
+                         'Females', 'Males'),
+           month = str_sub(info, 4, 4),
+           day = str_sub(info, 5),
+           date = lubridate::mdy(paste(month, day, '2006')),
+           catch = catch * 3)
+
+# Plot figure -----------------
+
+# Generate figure
+population_figure <- ggplot(daily_trap_catch, aes(x = date, y = catch, shape = sex, 
+                     color = sex, linetype = sex, fill = sex)) + 
+    stat_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) + 
+    geom_point(alpha = 0.48) + 
+    scale_color_grey() +
+    scale_fill_grey() + 
+    scale_x_date(expand = c(0,0)) +
+    labs(x = '', y = 'Onion Maggot Trap Catch') + 
+    pest_management_science + 
+    theme(legend.position = c(0.85, 0.75),
+          axis.line.x = element_line(size = 0.48, linetype = 'solid', 
+                                     color = 'black'),
+          axis.line.y = element_line(size = 0.48, linetype = 'solid', 
+                                     color = 'black'))
+
+# Save Figure
+ggsave(plot = population_figure,
+       filename = './figures/raw-figures/figure0_population_figure.pdf',
+       width = 5, height = 3)

### 2019-08-21 analysis/om-spinosad-lab-time-dose.R

@@ -1,0 +1,253 @@
+##############################################
+#                                            #
+#       Onion Maggot Spinosad                #
+#           Lab Trials                       #
+#                                            #
+##############################################
+
+
+# ACET Lab + Nault Lab @ Cornell AgriTech
+# May 2019
+
+# Load Libraries and other resources --------------
+library(tidyverse)
+library(car)
+library(emmeans)
+library(ggpubr)
+source('./analysis/model_diagnostics.R')
+source('./analysis/pest_management_science_theme.R')
+
+# Load Data ------------------
+
+lab_trial_2006 <- read_csv('./data/om-spinosad-lab-time-dose-trial-2006.csv', 
+                           skip = 8)
+
+# Preprocess data ------------------
+
+# Pull out just the mortality by day for 2006 trial
+mortality_2006 <- lab_trial_2006 %>% 
+    select(replication, rate, period, 
+           contains('female_'), contains('male_')) %>% 
+    gather(key = 'evaluation', value = 'mortality', 
+           -replication, -rate, -period) %>% 
+    separate(evaluation, c('sex', 'day'))
+
+# Pull out just the survivors for 2006
+survivors_2006 <- lab_trial_2006 %>%
+    select(replication, rate, period,
+           contains('total_alive')) %>% 
+    gather(key = 'type', value = 'alive', 
+           contains('total_alive')) %>% 
+    separate(type, c('total', 'status', 'sex')) %>% 
+    select(-total, -status)
+
+# Combine mortality and survivorship data
+trial_2006 <- left_join(mortality_2006, survivors_2006)
+
+# Model 2006 Data ---------------------
+
+# Translate periods into number of months spheres left in the field
+period_time_info <- tibble(period = c('JUN', 'JUL', 'AUG', 'SEP'),
+                 month = 1:4)
+
+# 2006 Mortality Rate
+mortality_rate_2006 <- trial_2006 %>% 
+    group_by(replication, rate, period, sex) %>% 
+    summarize(dead = sum(mortality),
+              alive = first(alive)) %>% 
+    mutate(total = dead + alive,
+           mortality_rate = dead/total) %>% 
+    left_join(period_time_info) %>% 
+    mutate(labels = factor(rate, levels = c('CK', 'LO', 'HI'),
+                           labels = c('No Spinosad', 
+                                      '0.5% Spinosad', 
[…]

### 2019-08-21 analysis/om_color_trials_2005.R

@@ -1,95 +1,0 @@
-#########################################
-#                                       #
-#       Onion Maggot Color Trials       #
-#                                       #
-#########################################
-
-
-# ACET Lab + Nault Lab @ Cornell AgriTech
-# May 2019
-
-# Load Libraries and other resources --------------
-
-library(tidyverse)
-library(car)
-library(emmeans)
-source('./analysis/model_diagnostics.R')
-source('./analysis/appl_ent_figure_theme.R')
-
-
-# Dato Processing ----------------------------
-
-# Load data for color trial
-color_trials <- read_csv('./data/om_color_trials_2005.csv', skip = 19)
-
-# Information on treatments documented in csv file
-treatment_info <- tibble(
-    treatment = c(8, 10,11,12),
-    color = factor(c('White',
-              'Yellow',
-              'Green',
-              'Red'),
-              levels = c('White',
-                         'Yellow',
-                         'Green',
-                         'Red'))
-)
-
-# Reshape the data and join with treatment information
-color_trial_treatment <- color_trials %>% 
-    gather(sex, flies, males, females) %>%
-    left_join(treatment_info)
-
-# Modeling --------------------------
-
-# Linear model relating sex and color to fly catch
-color_mod <- lm(flies ~ sex * color, data = color_trial_treatment)
-
-# Print and plot model diagnostics
-# model_diagnostics(color_mod) # Run to see plots
-model_diagnostics(color_mod, to_plot = FALSE)
-
-# Non-normality and slight heteroscedascity detected
-# Square root transform applied
-color_mod_transform <- lm(sqrt(flies) ~ sex * color, data = color_trial_treatment)
-
-# Model diagnostics of new model - resolved issues
-# model_diagnostics(color_mod_transform) # Run to see plots
-model_diagnostics(color_mod_transform, to_plot = FALSE)
-
-# Contrasts and post-hoc tests
-emmeans(color_mod_transform, ~ sex * color, type = 'response') %>% 
-    contrast(method = 'dunnett', by = 'sex')
-
-emmeans(color_mod_transform, ~sex * color, type = 'response') %>%
-    contrast(method = 'tukey', by = 'color')
-
-# Figure generation -----------------------------
-
-# Set plotting parameters
-dodge_width = 0.48
-jitter_width = 0.12
-
-# Set seed for reproducibility
-set.seed(72)
-
-# generate figure
[…]

### 2019-08-21 analysis/om_delia_lure_2006.R

@@ -1,60 +1,0 @@
-##############################################
-#                                            #
-#       Onion Maggot Delia Lure Trials       #
-#                                            #
-##############################################
-
-
-# ACET Lab + Nault Lab @ Cornell AgriTech
-# May 2019
-
-# Load Libraries and other resources --------------
-
-library(tidyverse)
-library(car)
-library(emmeans)
-source('./analysis/model_diagnostics.R')
-source('./analysis/appl_ent_figure_theme.R')
-
-
-# Dato Processing ----------------------------
-
-# Load data for color trial
-delia_lure_trial <- read_csv('./data/om_delia_lure_2006.csv', skip = 9) %>% 
-    # reported numbers are total counts for four sticky cards divided by four.
-    # we'll multiply by 4 to bring back to total counts.
-    mutate(total_onion_maggot = as.integer(onion_maggot * 4)) %>% 
-    select(-onion_maggot)
-
-# Reformat for t-test
-prep_ttest <- delia_lure_trial %>% spread(treatment, total_onion_maggot)
-
-# Modeling --------------------------
-
-# Paired t-test by location and day
-t.test(prep_ttest$Baited, prep_ttest$Unbaited, paired = TRUE)
-
-# Check for normality
-qqPlot(delia_lure_trial$total_onion_maggot)
-
-# Figure generation -----------------------------
-
-# Set seed for reproducibility
-set.seed(24)
-
-# Generate figure
-delia_lure_figure <- ggplot(delia_lure_trial, aes(x = treatment, y = total_onion_maggot)) + 
-    stat_summary(fun.data = 'mean_cl_boot', 
-                 geom = 'errorbar',
-                 width = 0.24) +
-    stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'point') + 
-    geom_point(position = position_jitter(0.12),
-               alpha = 0.48) + 
-    labs(x = 'Treatment', y = 'Total Onion Maggot Fly Adults') +
-    applied_entomology_theme
-
-# Save figure
-ggsave(plot = delia_lure_figure,
-       filename = './figures/raw/delia_lure_figure.pdf',
-       width = 4, height = 3)

### 2019-08-21 analysis/om_shape_trials_2005.R

@@ -1,109 +1,0 @@
-##############################################
-#                                            #
-#       Onion Maggot Shape Trials            #
-#                                            #
-##############################################
-
-
-# ACET Lab + Nault Lab @ Cornell AgriTech
-# May 2019
-
-# Load Libraries and other resources --------------
-library(tidyverse)
-library(car)
-library(emmeans)
-source('./analysis/model_diagnostics.R')
-source('./analysis/appl_ent_figure_theme.R')
-
-
-# Dato Processing ----------------------------
-
-# Load data for shape trial
-shape_trial_results <- read_csv('./data/om_shape_trials_2005.csv', skip = 17)
-
-# Shape treatment info from csv file
-treatment_info <- tibble(
-    treatment = 1:5,
-    treatment_shape = factor(c('Short Cylinder',
-                        'Tall Cylinder',
-                        'Cube',
-                        'Square Panel',
-                        'Sphere'
-                        ),
-                        levels = c('Short Cylinder',
-                                   'Sphere',
-                                   'Cube',
-                                   'Square Panel',
-                                   'Tall Cylinder'
-                        ))
-)
-
-# Reshape the data and join with treatment information
-shape_trial <- shape_trial_results %>% 
-    gather(key = sex, value = flies, -treatment, -replication) %>% 
-    left_join(treatment_info)
-
-
-# Modeling --------------------------
-
-# Linear model relating sex and color to fly catch
-shape_mod <- lm(flies ~ sex * treatment_shape, data = shape_trial)
-
-# Print and plot model diagnostics
-# model_diagnostics(shape_mod) # Run to see plots
-model_diagnostics(shape_mod, to_plot = FALSE)
-
-# Based on diagnostics, there seems to be an outlier
-outlierTest(shape_mod) # check outlier
-
-# Remodel with outlier removed
-shape_mod_xoutlier <- lm(flies ~ sex * treatment_shape, data = shape_trial[-31,])
-
-# Print and plot model diagnostics
-# model_diagnostics(shape_mod_xoutlier) # Run to see plots
-model_diagnostics(shape_mod_xoutlier, to_plot = FALSE)
-
-# Contrasts and post-hoc tests
-emmeans(shape_mod_xoutlier, ~sex ) %>% contrast(method = 'tukey')
-
[…]

### 2019-08-21 analysis/om_size_trials.R

@@ -1,110 +1,0 @@
-#########################################
-#                                       #
-#       Onion Maggot Size Trials       #
-#                                       #
-#########################################
-
-
-# ACET Lab + Nault Lab @ Cornell AgriTech
-# May 2019
-
-# Load Libraries and other resources --------------
-
-library(tidyverse)
-library(car)
-library(emmeans)
-source('./analysis/model_diagnostics.R')
-source('./analysis/appl_ent_figure_theme.R')
-
-
-# Dato Processing ----------------------------
-
-# Load data for 2005 size trial
-size_trial_2005 <- read_csv('./data/om_size_trials_2005.csv', 
-                            skip = 25)
-
-# Information on treatments documented in csv file
-treatment_info_2005 <- tibble(
-    treatment = 5:9,
-    #size is diameter of sphere in centimeters
-    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
-                  levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
-)
-
-# Reformat 2005 data, add in treatment and year information
-size_trial_treatment_2005 <- size_trial_2005 %>% 
-    gather(sex, flies, males, females) %>% 
-    left_join(treatment_info_2005) %>% 
-    mutate(year = '2005') %>% 
-    select(sex, size, flies, year)
-
-
-# Load data for 2006 size trial
-size_trial_2006 <- read_csv('./data/om_size_trials_2006.csv', 
-                            skip = 16, col_types = c('ccccii'))
-
-# Information on treatments documented in csv file
-treatment_info_2006 <-tibble(
-    treatment = as.character(6:10),
-    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
-                  levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
-    )
-
-# Reformat 2006 data, add in treatment and year information
-size_trial_treatment_2006 <- size_trial_2006 %>% 
-    select(-size) %>% 
-    gather(sex, flies, females, males) %>% 
-    left_join(treatment_info_2006) %>%
-    mutate(year = '2006') %>% 
-    select(sex, size, flies, year)
-
-# Combine years
-size_trial <- bind_rows(size_trial_treatment_2006, size_trial_treatment_2005)
-
-# Modeling --------------------------
-
-# Linear model relating sex and color to fly catch
[…]

### 2019-08-21 analysis/om_size_trials_2005.R

@@ -1,55 +1,0 @@
-library(tidyverse)
-library(car)
-library(emmeans)
-source('./analysis/model_diagnostics.R')
-
-
-size_trial <- read_csv('./data/om_size_trials_2005.csv', 
-                       skip = 25)
-
-treatment_info <- tibble(
-    treatment = 5:9,
-    #size is diameter of sphere in centimeters
-    size = factor(c('7.5', '5.0', '6.25', '8.75', '10.0'),
-                         levels = c('10.0', '8.75', '7.5', '6.25', '5.0'))
-)
-
-size_trial_treatment <- size_trial %>% 
-    gather(sex, flies, males, females) %>% 
-    left_join(treatment_info)
-
-size_mod <- lm(flies ~ sex * size, data = size_trial_treatment)
-
-model_diagnostics(size_mod)
-
-emmeans(size_mod, ~ sex * size) %>% contrast(by = 'sex', method = 'dunnett')
-emmeans(size_mod, ~ sex * size) %>% contrast(simple = 'sex', method = 'tukey')
-emmeans(size_mod, ~ sex * size) %>% cld(details = TRUE)
-
-stat_labels <- emmeans(size_mod, ~ sex * size) %>% 
-    cld() %>% data.frame() %>% 
-    filter(sex == 'females') %>% 
-    mutate(label = c('B', 'B', 'AB', 'AB', 'A'))
-
-dodge_width = 0.48
-jitter_width = 0.12
-ggplot(size_trial_treatment, aes(x = size, y = flies, color = sex)) + 
-    stat_summary(fun.data = 'mean_cl_boot', 
-                 geom = 'errorbar',
-                 position = position_dodge(dodge_width),
-                 width = dodge_width/2) +
-    stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'point',
-                 position = position_dodge(dodge_width)) +
-    geom_point(position = position_jitterdodge(dodge.width = dodge_width,
-                                               jitter.width = jitter_width),
-               alpha = 0.48) + 
-    geom_text(data = stat_labels, 
-              aes(x = size, y= 72, label = label),
-              show.legend = FALSE) + 
-    scale_color_grey() + 
-    theme_bw() + 
-    labs(x = 'Sphere Trap Diameter (cm)', y = 'Onion Maggot Fly Adults') + 
-    theme(legend.title = element_blank(),
-          legend.position = c(0.75, 0.75),
-          legend.background = element_rect(color = 'grey30'))

### 2019-08-21 analysis/pest_management_science_theme.R

@@ -1,4 +1,4 @@
-############################
+###########################
 #                          #
 #       Figure Theme       #
 #                          #
@@ -8,7 +8,7 @@
 # ACET Lab + Nault Lab @ Cornell AgriTech
 # May 2019
 
-applied_entomology_theme <- theme_bw() +
+pest_management_science <- theme_bw() +
     theme(legend.background = element_rect(color = 'grey30'),
           panel.border = element_blank(),
           panel.grid = element_blank(),
@@ -17,6 +17,5 @@ applied_entomology_theme <- theme_bw() +
           axis.line.y = element_line(size = 0.48, linetype = 'solid', 
                                      color = 'black'),
           legend.margin = ggplot2::margin(1.24, 1.24, 1.24, 1.24),
-          legend.title = element_blank(),
-          legend.position = c(0.75, 0.75)
-          )
+          legend.title = element_blank()
+    )

### 2019-08-21 manuscript/pest-management-science/main.tex
updated manuscript title
added figures to manuscript

@@
 
-\title{title}
+\title{Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})}
 
@@
 
+\paragraph{Population Monitoring}
+
+\paragraph{Onion Maggot Mortality}
+
+\paragraph{Field Damage}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/final-figures/figure-1.pdf}
+\caption{Population dynamics of adult onion maggot (\textit{D.
+antiqua} flies in upstate New York muck regions.
+Points indicate observations of numbers of adult flies captured on sticky cards.
+Lines and shaded regions indicate smoothed fits and 95\% confidence intervals respectively.
+}
+\label{fig:figure1}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/final-figures/figure-2.pdf}
+\caption{Adult onion maggot (\textit{D.
+antiqua} mortality in the presence of spinosad treated spheres.
+(A) Raw data of effects of exposure time and spinosad rate on mortality of adult onion maggot flies.
+Light points indicate individual observations.
+Solid points and error bars denote mean and 95\% confidence intervals respectively.
+(B) Main effects of spinosad rate on adult onion maggot mortality.
+Points and error bars denote mean effect and 95\% confidence intervals respectively.
+(C) Main effect of exposure time on adult onion maggot mortality.
+Line and shaded area denote effect and 95\% confidence region respectively.
+(D) Photographs of spinosad treated spheres at increasing exposure time in field conditions.
+Spheres were placed in the field on the 15th of May.
+}
+\label{fig:figure2}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/final-figures/figure-3.pdf}
+\caption{Adult onion maggot fly mortality following introduction to cages containing spinosad treated spheres.
+Spheres were treated with differing rates of spinosad (rows) and exposed to field conditions for increasing amounts of time (column).
+Lines and shaded regions indicate fitted smoothed (LOESS) mortality rates and 95\% confidence regions respectivel.
+}
+\label{fig:figure3}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/final-figures/figure-4.pdf}
+\caption{Field damage of onions.
+(A) End of season stand loss of onions (number of dead onion maggot plants) as a result of all mortality factors.
+(B) Cumulative damage (number of dead onion maggot plants) as a result of onion maggot larval feeding.
+Light points indicate observed values.
+Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.
+}
+\label{fig:figure4}
+\end{figure}
+
 \paragraph{Shape Trial} Models relating trap shape and \textit{D.

### 2019-08-29 manuscript/pest-management-science/main.tex
Added additional figure and began methods

@@
 
-\subsection{Field Trials}
+Field trials evaluating the efficacy of attract and kill strategies to manage onion maggot populations were conducted from 2006 to 2008 in commercial dry bulb onion fields on muck soils in upstate New York.
+Muck soils are high organic matter soils formed from old lake beds.
+Trials were conducted from May to September.
 
-\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
-Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.
-Traps were placed in the field in late May then collected in late June.
+\subsection{Population Monitoring}
 
-\paragraph{Size Trial}
-To evaluate the influence of trap size on the trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm diameter were placed along the long edge of onion fields with spacing 15.24 meters apart in a randomized controlled block design with five replications.
+Population monitoring of onion maggot adults was accomplished by deploying white sticky cards with six replications in experimental plots.
+Cards were collected weekly and the number of males and females counted.
 
-\paragraph{Color Trial}
-To evaluate the effect of color on trap catch and monitoring of adult onion maggot fly, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.
+\subsection{Onion Maggot Mortality}
 
-\paragraph{Delia Lure Trial}
-To evaluate the effect of adding an attractant an trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
-Trap Catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
+The ability of spinosad spheres to kill onion maggot flies was
+
+\subsection{Field Damage}
 
@@
 Points and error bars denote mean effect and 95\% confidence intervals respectively.
+Different letters denote significant differences (p \textless 0.05).
 (C) Main effect of exposure time on adult onion maggot mortality.
@@
 \caption{Field damage of onions.
-(A) End of season stand loss of onions (number of dead onion maggot plants) as a result of all mortality factors.
-(B) Cumulative damage (number of dead onion maggot plants) as a result of onion maggot larval feeding.
+(A) End of season stand loss of onions (number of dead onion plants) as a result of all mortality factors.
+(B) Cumulative damage (number of dead onion plants) as a result of onion maggot larval feeding.
 Light points indicate observed values.
 Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.
+Different letters denote significant differences (p \textless 0.05).
 }
@@
 
-\paragraph{Shape Trial} Models relating trap shape and \textit{D.
-antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (P \textless 0.001, $R^2_{adj}$ = 0.70, Table \ref{table:1}).
-Trap shape significantly influenced (P = 0.005) catch of adult \textit{D.
-antiqua} (Figure \ref{fig:figure1}).
-Sticky traps caught approximately 27.81 $\pm$ 2.8 more female flies than male flies.
-Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
-While there were no significant differences between females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
-No significant differences were observed between male trap catch.
-
-\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).
-Trap size significantly influenced trap catch (P \textless 0.001).
-Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.
-While male trap catch was less than that of females, trends in catch amoung the different diameters were similar for both males and females.
-
-\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.79, Table \ref{table:1}).
-Color significantly influenced trap catch (P \textless 0.001) with white traps catching significantly more females than any other color (t \textless -3.1, df = 32, P \textless 0.012) and significantly more males than any other color except yellow (t \textless -3.1, df = 32, P \textless 0.012, Yellow: t = -1.6, df = 32, P = 0.3).
-White traps caught significantly more females than males (t = 6.1, df = 32, P \textless 0.001).
-
-\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.
-Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/final-figures/figure-5.pdf}
+\caption{Field damage of onion in enclosed cages with differing spinosad sphere formulations.
+Cumulative damage is number of dead plants as a result of onion maggot damage.
+Points and error bars denote mean and 95\% confidence intervals respectively.
+Different letters denote significant differences (p \textless 0.05).
+}
+\label{fig:figure4}
+\end{figure}
 

### 2019-09-06 manuscript/pest-management-science/main.tex
First draft with abstract.

@@
 
+Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.
+Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.
+These options may not be viable in organic production systems or areas where resistant populations are developing.
+Here we explore the efficacy of an attract and kill strategy for control of onion maggot evaluating the ability of attractive spinosad containing spheres to kill adult onion maggots and reduce field losses.
+Spinosad containing spheres were able to consistently kill onion maggot adults over the course of the field season.
+Pairing spinosad spheres with Delia Lure increased efficacy of the attract and kill strategy.
+Performance of this strategy never achieved levels of control comparable with insecticide controls, but may be an additional tool in an integrated pest management approach where conventional pesticides are not available or additional control techniques are needed.
+
 % Please include a maximum of seven keywords
@@
 \section{Introduction}
+
+Allium crops worldwide suffer attack from onion maggot (\textit{Delia antiqua}).
+Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \citep{nault2006performance, nault2006onion}.
+Other allium crops including garlic (\textit{Allium sativem} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) are similarly susceptible\citep{ellis1979factors,ning2017predicting,nault2007ecology, }.
+Commercial onion production has relied upon intensive management of this pest, but losses continue to occur in places where crop rotation is not used and resistant populations are present \citep{martinson1988dispersal, nault2006onion}.
+
+The lifecycle of \textit{Delia antiqua} plays a large role in its severity as an onion pest.
+In the northern United States, three generations per year are common \citep{eckenrode1975population, hoepting2004insecticide}.
+While adults can be captured in fields using sticky cards, the larvae cause devastating damage through feeding on plant roots and onion bulbs \citep{nault2006onion, nault2006performance}.
+Feeding by onion maggot larvae early in the season can kill seedlings and damaged plants can become more susceptible to infection by pathogen and attack by subsequent generations \citep{eckenrode1986impact,nault2006performance}.
+Feeding by onion maggot larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the produce.
+
+Prophylatic insecticide applications at planting are the current tool of choice to manage this pest \citep{nault2006performance}.
+The seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500) is commonly used as is a cyromazine seed treatment with Chlorpyrifos drench \citep{nault2006performance}.
+Crop rotation, removal of damaged onions, and delayed planting can all be used to reduce onion maggot damage, but may not be the strategy of choice for large scale commercial growers \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
+
+Management of this pest has relied on prophylactic insecticide applications at planting \citep{nault2006performance}.
+A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
+Chlorpyrifos is commonly used as a drench treatment in combination with either cyromazine seed treatment (Trigard)  \citep{nault2006performance} or the seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500).
+Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective management tactics \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
+
+Recent efforts in monitoring onion maggot populations, however, have opened the possibility of a new control strategy for \textit{Delia antiqua}.
+Onion maggot adults respond to and are attracted by visual and chemical cues \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
+Visually, onion maggot adults tend to prefer large white spheres, while chemically they respond strongly to chemical constituents of decomposing onion.
+In particular, two components of decomposing onion, 2-phenyl-ethanol and n-valeric acid, are attractive and have been formulated into attractive lures \citep{ishikawa1984mixture,ishikawa1987controlled, kuhar2006field}.
+Combining the white spheres with the chemically attractive lures approximately doubled onion maggot trap catch \citep{willett2019}.
+Adding an insecticide to these attractive spheres could be an effective attract and kill solution for controlling onion maggot.
+
+Attract and kill strategies rely on pairing an attractive component, usually involving a semiochemical and/or visual component, with a killing component whether through mechanical or chemical means \citep{gregg2018advances}.
+Attract and kill strategies can be more specific and environmentally friendly and have contributed to integrated pest management of flies and moths \citep{gregg2018advances}.
+Of particular interest and inspiration for this work, red insecticide treated spheres have been developed as an attract and kill solution for control apple maggot in northeastern orchards \citep{bostanian2001attract,duan1995control}.
+
+Of particular consideration in developing an attract and kill solution for use in an integrated pest management program is choice of the killing component of the package.
+For working with onion maggot control, we elected to use Spinosad as an insecticidal killing component.
+Spinosad is a naturally derived neurotoxic insecticide originally isolated from the soil dwelling actinomycete \textit{Saccharopolyspora spinosa} \citep{racke2007reduced}.
+It has been approved for use on over 150 fruit and vegetable crops in the United States and is certified for use in organic production by the USDA National Organic Standards Board and Organic Materials Review Institute (OMRI) \citep{racke2007reduced,williams2003naturally}.
+In addition, spinosad has substantially lower non-target effects relative to conventional pesticides and low residual toxicity \citep{williams2003naturally}.
+Because of its complementary nature to current conventional management of onion maggot and potential use in organic production systems, spinosad was included in development of an attract and kill solution for onion maggot.
+
+To develop an effective attract and kill solution to control onion maggot, we combined attractive white spheres developed in previous work \citep{willett2019} with a spinosad insecticide solution and evaluated the ability of these spinosad attractive spheres to kill adult onion maggot flies and reduce damage to onions over the course of three field seasons in upstate New York.
+
 \section{Materials and Methods}
@@
 
-Population monitoring of onion maggot adults was accomplished by deploying white sticky cards with six replications in experimental plots.
-Cards were collected weekly and the number of males and females counted.
+Population monitoring of onion maggot adults was accomplished by deploying white sticky cards in triplicate with six replications in control areas of experimental plots deployed using a randomized controlled block design.
+Cards were collected weekly from May to September and the number of male and female adult flies counted.
 
@@
 
-The ability of spinosad spheres to kill onion maggot flies was
+Because white spheres has previously been shown to be attractive to onion maggot adults, 1\%, 0.5\%, and 0\% (control) spinosad were added to paraffin and coated on 8.75cm diameter white plastic spheres to evaluate the ability of the spheres to cause onion maggot mortality.
+Additionally, the temporal efficacy of the spinosad solution was evaluated.
+
+To do so, the ability of spinosad spheres to kill onion maggot flies was evaluated over the course of multiple field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate climate and dose effects.
+Spheres had three levels of spinosad: No Spinosad (Control), 0.5\% Spinosad, and 1\% Spinosad.
+Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively.
+Deployment in the field followed a randomized controlled block design.
+
+Following recovery from the field, spheres were photographed to document degradation, then immediately suspended in ~25cm x 25cm x 50cm screen and plexiglass cages containing water in a petri dish.
+Ten male and ten female onion maggot flies were then introduced to each cage and mortality monitored every 24 hours for 72 hours.
+This trial was conducted for both spinosad  containing and control spheres.
+Six replications of each treatment, exposure combination was conducted.
 
@@
 
+To evaluate the efficacy of attract and kill techniques in controlling onion maggot damage, field damage from onion maggot larvae was monitored throughout the season.
+Onion seed of \textit{Allium cepa} L.
+'Arsenal', an early yellow globe variety, was planted in late April with plants subjected to six treatments in a randomized controlled block design.
+Insecticide treated plants were treated at planting with a seed treatment package package containing thiamethoxam, spinosad and several fungicides (FarMore FI500).
+This was placed in the experiment to be a positive control.
+No insecticide treated plants did not receive the seed treatment package and did not receive any attract and kill strategies.
+Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as and attract and kill solution.
+White sticky cards with and without attractive Delia Lures were also deployed.
+Four replications of each treatment combination were evaluated.
+
+Each individual experimental plot was 8 rows by 30 feet long separated from its nearest neighboring experimental plot by a minimum of 100 feet in any direction.
+Three weeks following planting, seedlings in the middle two rows were counted to obtain an initial stand count.
+Following initial stand count, plant loss due to damage by onion maggot larvae was evaluated on a weekly basis in the middle two rows until the end of season when a final stand count was taken (including all mortality factors).
+Plant loss due to onion maggot was assessed visually then confirmed by removing the plant and ascertaining presence of onion maggot larvae.
+
+\subsection{Enhanced Formulation}
+
+To enhance attractiveness, longevity, and performance of spinosad baited spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate.
+The efficacy of this new formulation was compared to spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials.
+Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisting of four rows on onion by 30ft long.
+Plots were seeded in early May and each plot was caged using PVC pipe and screen mesh.
+One hundred fifty adult flies with a 50:50 male to female ratio were released into each cage on the second of June and nine days later on June 11th.
+As described above, Initial and final stand counts were taken and plant damage due to onion maggot larvae evaluated on a weekly basis.
+
 \subsection{Analysis}
+
+To evaluate population dynamics of onion maggot over time, a smoothing function consisting of a generalized additive model with cubic splines was fitted to the raw population numbers for visual display.
+
+To evaluate adult onion maggot mortality as a result of contact with spheres containing spinosad, linear models and analysis of variance were used.
+Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
+Main effects were teased out from interactions using Tukey and Dunnett post-hoc tests.
+
+Field damage and stand loss were evaluated using mixed effects linear and negative binomial models.
+Best fit models were selected after consideration of data distributions, residual diagnostics, likelihood ration considerations, information criteria, and psuedo-$R^2$ values, root mean squared error and coefficient of variation of root mean squared error.
+
 \subsection{Data Management}
+
+All data for the trials were entered into flat tabular (.csv) files.
+All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.
+The $tidyverse$, $car$, $lme4$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, lme, emmeans}.
+All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-control).
 
@@
 
+During the field seasons monitored in these trials in upstate New York, \textit{Delia antiqua} had three generations (Figure \ref{fig:figure1}).
+The first population of adults peaked in June, the second in late July, and the third in August.
+More males than females were collected on sticky cards, but both males and females followed roughly the same population cycles.
+
 \paragraph{Onion Maggot Mortality}
 
+White spheres baited with spinosad caused appreciable mortality of onion maggot adults (Figure \ref{fig:figure2}A).
+Both spinosad rate (F =114.3, df=2, p \textless 0.001)  and exposure time (F = 4.7, df = 1, p = 0.03) in the field significantly explained approximately 62\% of the observed variation in adult onion maggot mortality ($R^2_{adj}$ = 0.62, p \textless 0.001).
+Both rates of spinosad treated spheres caused approximately 47$\pm$4\% more onion maggot mortaliy than untreated controls (Figure \ref{fig:figure2}B).
+Increasing rates of spinosad from 0.5\% to 1\% did not signifcantly increase onion maggot mortality (Figure \ref{fig:figure2}B).
+
+Increasing time spent in the field did tend to decrease efficacy of spinosad containing spheres (Figure \ref{fig:figure2}C).
+For every month of exposure, mortality of onion maggot tended to decline 3$\pm$1\%.
+After four months of exposure, and despite obvious degradation of the parafin containing the spinosad (Figure \ref{fig:figure2}D), onion maggot mortality as a result of contacting spinosad baited spheres still remained above 45\% (Figure \ref{fig:figure2}C).
+
+Onion maggot mortality as a result of contacting spinosad containing spheres was not constant over the 72 hours of monitoring in cages (Figure \ref{fig:figure3}).
+For both spinosad rates, onion maggot mortality tended to peak at around 48 hours for spheres with one month exposure to field conditions (the June cohort).
+After longer exposure to field conditions, onion maggot mortality tended to decline over the course of 72 hours.
+
 \paragraph{Field Damage}
+
+Deployment of the attract and kill solution of spinosad baited spheres did not substantially affect end of season onion loss as a result of all mortality factors (Figure \ref{fig:figure4}A), but did influence cumulative damage as a result of onion maggot larval feeding (Figure \ref{fig:figure4}B).
+Treatment solution (Insecticide, No Insectide, Spinosad Sphere, Sticky Card) significantly (F = 5.8, df = 3, p = 0.005) explained approximately 38\% of the observed variation in end of season onion stand loss as a result of all mortality factors ($R^2_{adj}$ = 0.38, p = 0.005, Figure \ref{fig:figure4}A).
+The presence of Delia Lure did not significantly (p \textgreater 0.05) affect end of season onion stand loss.
+Insecticide treatment worked best at preventing end of season stand loss (Figure \ref{fig:figure4}A).
+The no insecticide treatment was highly variable and not significantly (p \textgreater 0.05)  different from insecticide controls.
+Spinosad and sticky card treatments were not significantly different from no insecticide treatments, but were significantly worse than insecticide controls.
+
+Cumulative damage as a result of onion maggot larval feeding was significantly explained by treatment solution ($\chi^2$ = 42.2, df = 3, p \textless 0.001), the presence of Delia Lure ($\chi^2$ = 10.0, df = 1, p = 0.001), and their interaction ($\chi^2$ = 21.4, df = 1 p \textless 0.001).
+Cumulative damage due to feeding by onion maggot larvae over the course of the field seasons ranged from 0 in some control plots to 82 dead onion maggot plants in a few plots.
+This amounts to approximately 20-30\% losses of onion directly attributable feeding by onion maggot larvae.
+All treatments were significantly worse than insecticide controls which had very low levels of onion maggot damage (Figure \ref{fig:figure4}B).
+Pairing Delia Lure with spinosad containing spheres significantly reduced damage by onion maggot larvae by 72$\pm$10\% (p \textless 0.001) compared to spinosad spheres alone.
+Pairing Delia Lure with sticky cards had the opposite effect (Figure \ref{fig:figure4}B).
+
+\paragraph{Enhanced Formulation}
+
+Treatment significantly explained observed onion maggot damage in field cage trials with the enhanced formulation ($\chi^2$ = 23.9, df = 2, p \textless 0.001).
+The enhanced formulation (Spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different than Spinosad only treatments with 0.5\% spinosad containing spheres.
+Both treatments containing spinosad performed significantly better than No insecticide controls (p \textless 0.05).
 
@@
 \caption{Population dynamics of adult onion maggot (\textit{D.
-antiqua} flies in upstate New York muck regions.
+antiqua}) flies in upstate New York muck regions.
 Points indicate observations of numbers of adult flies captured on sticky cards.
@@
 }
-\label{fig:figure4}
+\label{fig:figure5}
 \end{figure}
@@
 
+Using spinosad baited spheres as an attract and kill solution for control of onion maggot populations may be an effective tool under an integrated pest management approach.
+Over the course of the three field seasons, with three generations per year (Figure \ref{fig:figure1}), the attract and kill solution was able to consistently inflict mortality on adult onion maggot flies, even after prolonged exposure to field conditions (Figure \ref{fig:figure2}).
+While exposure did tend to reduce efficacy (Figure \ref{fig:figure2}C) and change the dynamics of mortality (Figure \ref{fig:figure3}), any effects were marginal and may be due to melting of the paraffin solution containing the spinosad (Figure \ref{fig:figure2}D).
+
+Importantly for practical use of this technique, higher doses of spinosad did not have noticeable effects on onion maggot mortality.
+The low rate of spinosad containing spheres resulted in adult onion maggot mortality that was not significantly different than mortality resulting from contact with spheres containing higher levels of spinosad (Figure \ref{fig:figure2}B).
+This suggests that inclusion of spinosad as the insecticide component of this attract and kill technique was not only an effective choice for implementation of an attract and kill strategy, but also is a viable option even at low doses.
+
+Using field onion maggot population averages and mortality achieved by spheres over time, numbers of adult onion maggots killed as a result of the attract and kill strategy can be estimated.
+During peak flights, approximately 272 onion maggot adults (both males and females) were caught on average per week.
+Over the course of the field season, approximately 64 adults were caught by sticky cards on average per week.
+Assuming spinosad baited spheres kill approximately 54\% of the adults they contact, over the course of a 16 week season, this attract and kill solution could have killed approximately 553 onion maggot adults (16 weeks x 64 adults on average per week * 0.54 mortality) per spinosad containing sphere.
+
+Although spinosad containing spheres were able to kill large numbers of onion maggot adults, the attract and kill solution did not appreciably affect end of season onion loss when all mortality factors were considered.
+These other mortality factors include climatic effects, pathogen infection, and attack by other insect pests such as onion thrips.
+The attract and kill solution did appreciably affect onion mortality due to feeding by \textit{Delia antiqua} larvae, however.
+
+The juxtaposition of these two results baselined against insecticide positive control and no insecticide negative controls suggests that insecticide treatments may be reducing other mortality factors in addition to controlling some damage by onion maggot larvae.
+Spinosad spheres in conjunction with the attractive Delia Lure resulted in levels of damage almost as good as insecticide controls, but with variation that led to overlap with no insecticide negative controls.
+In caged field trials, spinosad spheres reduced damage resulting from onion maggot feeding to below that of no insecticide controls.
+Interestingly, pairing Delia Lure with sticky cards produced higher levels of damage.
+This is likely because the kill part of the attract and kill sticky card solution was ineffective; delia lures likely attracted adult fly populations to plots but sticky cards did not cause sufficient mortality.
+Augmenting spinosad spheres with ammonium carbonate and casein hydrolysate did not appreciably change control with this attract and kill method.
+
+While not as effective as insecticide controls using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
+Spinosad spheres do cause adult onion maggot mortality over extended field seasons.
+This attract and kill approach could be used as an additional mortality factor in longer term management of onion maggot populations.
+In situations where immediate reduction in damage from onion maggot is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.
+
 \section*{Acknowledgements}
-Suggestions for acknowledgements?
+We appreciate technical assistance by M.
+Hessney and Delia Lure contributions from J.
+Meneley.
+The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.
 
@@
 \section*{Data Availability Statement}
-All code and data, including manuscript documentation, is available on GitHub(https://github.com/acetworld/onion-maggot-attraction).
+All code and data, including manuscript documentation, is available on GitHub(https://github.com/acetworld/onion-maggot-control).
 

### 2019-09-11 manuscript/pest-management-science/main.tex
updated and revised based on initial feedback

@@
 
-\title{Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})}
+\title{Attract and kill: Spinosad baited spheres to control onion maggot (\textit{Delia antiqua})}
 
@@
 These options may not be viable in organic production systems or areas where resistant populations are developing.
-Here we explore the efficacy of an attract and kill strategy for control of onion maggot evaluating the ability of attractive spinosad containing spheres to kill adult onion maggots and reduce field losses.
+Here we explore the efficacy of an attract and kill strategy for control of onion maggot evaluating the ability of attractive, spinosad containing spheres to kill adult onion maggots and reduce field losses.
 Spinosad containing spheres were able to consistently kill onion maggot adults over the course of the field season.
 Pairing spinosad spheres with Delia Lure increased efficacy of the attract and kill strategy.
-Performance of this strategy never achieved levels of control comparable with insecticide controls, but may be an additional tool in an integrated pest management approach where conventional pesticides are not available or additional control techniques are needed.
+Performance of this strategy can reduce damage by onion maggot larvae compared to no insecticide controls, but did not achieved levels of control comparable with insecticide treatment.
+Implementation of this attract and kill strategy could be a valuable tool in situations where conventional pesticides are not available, where additional control techniques are needed, or for longer term population control of onion maggot.
 
@@
 
-While not as effective as insecticide controls using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
+While not as effective as insecticide controls, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
 Spinosad spheres do cause adult onion maggot mortality over extended field seasons.
-This attract and kill approach could be used as an additional mortality factor in longer term management of onion maggot populations.
 In situations where immediate reduction in damage from onion maggot is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.
+Additionally, this attract and kill approach could be used as a control option where conventional pesticides are no longer effective or available.
+This strategy could also hold promise as an additional mortality factor in longer term management to control onion maggot populations.
 

### 2019-09-19 manuscript/pest-management-science/main.tex
Updated with comments from authors

--- 2019-08-29 manuscript/pest-management-science/main.tex
@@
 
-\title{Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})}
+\title{Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})}
 
@@
 \author[1\authfn{1}]{Camila C. Filgueiras}
-\author[2]{Starker Wright}
 \author[1]{Jan P. Nyrop}
@@
 \affil[1]{Department of Entomology, Cornell AgriTech, Cornell University, Geneva, NY, 14456, USA}
-\affil[2]{Bartlett Tree Experts, Dublin, PA, USA}
 
@@
 
+Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.
+Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.
+These options may not be viable in organic production systems or areas where insecticide-resistant populations occur.
+Here we explore the efficacy of an attract and kill strategy for control of \textit{D.
+antiqua} evaluating the ability of attractive, spinosad containing spheres to kill adult \textit{D.
+antiqua} and reduce crop losses.
+Spinosad containing spheres were able to consistently kill \textit{D.
+antiqua} adults over the course of the field season (mortality range: between 49\% and 59\% on average).
+Pairing spinosad spheres with Delia Lure increased efficacy by 72\% compared with the attract and kill strategy alone.
+Performance of this attract and kill strategy also can reduce damage by \textit{D.
+antiqua}  larvae in the field, but it did not achieve a level of control comparable to the level provided by a conventional insecticide treatment.
+Implementation of this attract and kill strategy could be a valuable tool in situations where conventional pesticides are either not available or desired, where additional control techniques are needed, or to provide a season-long option for control of \textit{D.
+antiqua} populations.
+
 % Please include a maximum of seven keywords
@@
 \section{Introduction}
+
+Allium crops worldwide suffer attack from onion maggot (\textit{Delia antiqua} Meigen).
+Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \citep{nault2006performance, nault2006onion}.
+Other allium crops including garlic (\textit{Allium sativum} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) are similarly susceptible \citep{ellis1979factors,ning2017predicting,nault2007ecology}.
+Commercial onion production has relied upon intensive management of this pest, but losses continue to occur in places where crop rotation is not used and insecticide-resistant populations are present \citep{martinson1988dispersal, nault2006onion}.
+
+The lifecycle of \textit{Delia antiqua} plays a large role in its severity as an onion pest.
+In the northern United States, three generations per year are common \citep{eckenrode1975population, hoepting2004insecticide}.
+In New York, \textit{D.
+antiqua} overwinters as a pupa and adults emerge in late April to early May and peak in late May to early June.
+The next generation begins to emerge in late June to early July and peaks in mid to late July, while the last generation adults begin to emerge in late July to early August and peak in mid to late August \citep{nault2011delaying}.
+While adults can be captured in fields using sticky cards, the larvae cause devastating damage by feeding on plant roots and onion bulbs \citep{nault2006onion, nault2006performance}.
+Feeding by \textit{D.
+antiqua} larvae early in the season can kill seedlings and damaged plants can become more susceptible to infection by pathogen and attack by subsequent generations \citep{eckenrode1986impact,nault2006performance}.
+Feeding by \textit{D.
+antiqua} larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the produce.
+
+Management of \textit{D.
+antiqua} has relied on prophylactic insecticide applications at planting \citep{nault2006performance}.
+A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
+Chlorpyrifos (Lorsban Advanced) is still commonly used as a drench treatment in combination with either cyromazine seed treatment (Trigard) \citep{nault2006performance,nault2006onion} or the seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500); although some growers rely exclusively on FarMore FI500 to manage \textit{D.
+antiqua}.
+Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective \textit{D.
+antiqua} management tactics \citep{martinson1988dispersal,finch1985influence,nault2011delaying} but they are not typically adopted by large-scale commercial growers.
+
+Recent advancements in monitoring \textit{D.
+antiqua} populations have created the possibility of a new control strategy.
+\textit{Delia antiqua} adults respond to and are attracted by visual and chemical cues \citep{harris1988host,harris1983color,thomingdeveloping,otto2000development}.
+Visually, \textit{D.
+antiqua} adults tend to prefer large white spheres, while chemically they respond strongly to chemical constituents of decomposing onion.
+In particular, two components of decomposing onion, 2-phenyl-ethanol and n-valeric acid, are attractive and have been formulated into attractive lures \citep{ishikawa1984mixture,ishikawa1987controlled,kuhar2006field}.
+Combining the white spheres with a chemically attractive lure, Delia Lure (AgBio, Westminster, CO), approximately doubled \textit{D.
+antiqua} adult trap catch \citep{willett2019}.
+Adding an insecticide to these attractive spheres could be an effective attract and kill solution for controlling \textit{D.
+antiqua}.
+
+Attract and kill strategies rely on pairing an attractive component, usually involving a semiochemical and/or visual component, with a killing component whether through mechanical or chemical means \citep{gregg2018advances}.
+Attract and kill strategies can be more specific and environmentally friendly and have previously contributed to integrated pest management of flies and moths \citep{gregg2018advances}.
+Of particular interest and inspiration for this work, red insecticide-treated spheres were developed as an attract and kill solution for control of apple maggot (\textit{Rhagoletis pomonella} (Walsh)) in northeastern orchards \citep{bostanian2001attract,duan1995control}.
+
+Choice of the killing component in an attract and kill solution for use in an integrated pest management program is important.
+For working with \textit{D.
+antiqua} control, we elected to use spinosad as the toxicant.
+Spinosad is a naturally derived neurotoxic insecticide originally isolated from the soil-dwelling actinomycete \citep{Saccharopolyspora spinosa} \citep{racke2007reduced}.
+It has been approved for use on over 150 fruit and vegetable crops in the United States and is certified for use in organic production by the USDA National Organic Standards Board and Organic Materials Review Institute (OMRI) \citep{racke2007reduced,williams2003naturally}.
+In addition, spinosad has substantially lower non-target effects relative to conventional pesticides and a low residual toxicity \citep{williams2003naturally}.
+Because of its complementary nature to current conventional management of onion maggot and potential use in organic production systems, spinosad was included in the development of an attract and kill solution for \textit{D.
+antiqua}.
+
+To develop an effective attract and kill solution to control \textit{D.
+antiqua}, we combined attractive white spheres developed in previous work \citep{willett2019} with a spinosad insecticide solution.
+We hypothesized that these spinosad-attractive spheres would kill \textit{D.
+antiqua} flies and significantly reduce maggot damage to onions.
+This study was conducted over the course of three field seasons in upstate New York.
+
 \section{Materials and Methods}
 
-Field trials evaluating the efficacy of attract and kill strategies to manage onion maggot populations were conducted from 2006 to 2008 in commercial dry bulb onion fields on muck soils in upstate New York.
+Field trials evaluating the efficacy of attract and kill strategies to manage \textit{D.
+antiqua} populations were conducted from 2006 to 2008 in commercial dry bulb onion fields on muck soils in upstate New York, USA.
 Muck soils are high organic matter soils formed from old lake beds.
@@
 
-Population monitoring of onion maggot adults was accomplished by deploying white sticky cards with six replications in experimental plots.
-Cards were collected weekly and the number of males and females counted.
+Population monitoring of \textit{D.
+antiqua} adults was accomplished by deploying white sticky cards in triplicate along onion field edges in each of six commercial onion fields.
+Field edges have been identified as ideal locations for trapping adult fly populations, especially when borders abut woodlands \citep{werling2006spatial}.
+Cards were collected weekly from May to September and the number of male and female adult flies counted.
 
-\subsection{Onion Maggot Mortality}
+\subsection{\textit{D. antiqua} Mortality}
 
-The ability of spinosad spheres to kill onion maggot flies was
+Because white spheres are highly attractive to \textit{D.
+antiqua} adults, 1\%, 0.5\%, and 0\% (control) spinosad were added to paraffin and coated on 8.75cm diameter white plastic spheres to evaluate the ability of the spheres to cause \textit{D.
+antiqua} mortality.
+Additionally, the temporal efficacy of the spinosad solution was evaluated.
+
+To do so, the ability of spinosad spheres to kill \textit{D.
+antiqua} flies was evaluated over the course of multiple field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate climate and dose effects.
+Spheres had three levels of spinosad: No spinosad (Control), 0.5\% spinosad, and 1\% spinosad.
+Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively.
+Deployment in the field followed a randomized controlled block design.
+
+Following recovery from the field, spheres were photographed to document degradation, then each one was immediately suspended in 25cm x 25cm x 50cm screen and plexiglass cages containing water in a petri dish.
+Ten male and ten female \textit{D.
+antiqua} flies were then introduced to each cage and mortality monitored every 24 hours for 72 hours.
+This trial was conducted for both spinosad containing and control spheres.
+Six replications of each of the 12 treatments (3 spinosad levels x 4 periods of field exposure) were conducted.
 
@@
 
+To evaluate the efficacy of attract and kill techniques for reducing \textit{D.
+antiqua} larval damage, onions killed or damaged by \textit{D.
+antiqua} larvae were monitored throughout the season.
+Onion seed of \textit{Allium cepa} L.
+’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to six treatments in a randomized controlled block design.
+Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package.
+This treatment was included in the experiment to be a positive control.
+Non-insecticide treated plants were grown from fungicide-only treated seeds and did not receive any attract and kill strategies.
+Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution.
+White sticky cards with and without attractive Delia Lure were also deployed.
+Four replications of each of the six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).
+
+Each individual experimental plot was 8 rows by 30 feet long separated from its nearest neighboring experimental plot by a minimum of 100 feet in any direction.
+Three weeks following planting, seedlings in the middle two rows were counted to obtain an initial stand count.
+Following initial stand count, plant loss due to damage by \textit{D.
+antiqua} larvae was evaluated on a weekly basis in the middle two rows until the end of season when a final stand count was taken (including all mortality factors).
+Plants killed by \textit{D.
+antiqua} were assessed visually, then confirmed by removing the plant and ascertaining presence of \textit{D.
+antiqua} larvae.
+When plants became too large to visually detect \textit{D.
+antiqua} damage, subsamples of plants were removed from the soil and bulbs inspected for \textit{D.
+antiqua} larvae and larval feeding damage.
+The overall percentage of cumulative \textit{D.
+antiqua} damaged plants for the season was determined.
+
+\subsection{Enhanced Formulation}
+
+To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate.
+The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials.
+Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows on onion each 12 ft long.
+All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i.
+/ 100 g seed).
+Seeds were planted in early May and each plot was caged using PVC pipe and screen mesh.
+One hundred fifty \textit{D.
+antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th.
+As described above, initial and final stand counts were taken and plant damage due to \textit{D.
+antiqua} larvae evaluated on a weekly basis.
+
 \subsection{Analysis}
+
+To evaluate population dynamics of \textit{D.
+antiqua} over time, a smoothing function consisting of a generalized additive model with cubic splines was fitted to the raw population numbers for visual display.
+
+To evaluate adult \textit{D.
+antiqua} mortality as a result of contact with spheres containing spinosad, linear models and analysis of variance were used.
+Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
+Main effects were teased out from interactions using Tukey and Dunnett post-hoc tests at $P < 0.05$.
+
+Field damage and stand loss were evaluated using mixed effects linear and negative binomial models.
+Best fit models were selected after consideration of data distributions, residual diagnostics, likelihood ration considerations, information criteria, and psuedo-$R^2$ values, root mean squared error and coefficient of variation of root mean squared error.
+
 \subsection{Data Management}
+
+All data for the trials were entered into flat tabular (.csv) files.
+All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.
+The $tidyverse$, $car$, $lme4$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, lme, emmeans}.
+All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-control).
 
@@
 
-\paragraph{Onion Maggot Mortality}
+During the period these trials were conducted in upstate New York, \textit{Delia antiqua} had three generations (Figure \ref{fig:figure1}).
+The first population of adults peaked in June, the second in late July, and the third in August.
+More males than females were collected on sticky cards, but both males and females followed roughly the same population cycles.
+
+\paragraph{\textit{Delia antiqua} Mortality}
+
+White spheres containing spinosad caused appreciable mortality of \textit{D.
+antiqua} adults (Figure \ref{fig:figure2}A).
+Both spinosad rate (F =114.3, df=2, p \textless 0.001)  and exposure time (F = 4.7, df = 1, p = 0.03) in the field significantly explained approximately 62\% of the observed variation in adult \textit{D.
+antiqua} mortality ($R^2_{adj}$ = 0.62, p \textless 0.001).
+Both rates of spinosad treated spheres caused approximately 47$\pm$4\% more \textit{D.
+antiqua} mortaliy than untreated controls (Figure \ref{fig:figure2}B).
+Increasing rates of spinosad from 0.5\% to 1\% did not signifcantly increase \textit{D.
+antiqua} mortality (Figure \ref{fig:figure2}B).
+
+Increasing time spent in the field decreased efficacy of spinosad containing spheres (Figure \ref{fig:figure2}C).
+For every month of exposure, mortality of \textit{D.
+antiqua} tended to decline 3$\pm$1\%.
+After four months of exposure, and despite obvious degradation of the paraffin containing the spinosad (Figure \ref{fig:figure2}D), \textit{D.
+antiqua} mortality as a result of contacting spinosad containing spheres still remained above 45\% (Figure \ref{fig:figure2}C).
+
+\textit{D.
+antiqua} mortality as a result of contacting spinosad containing spheres was not constant over the 72 hours of monitoring in cages (Figure \ref{fig:figure3}).
+For both spinosad rates, \textit{D.
+antiqua} mortality tended to peak at around 48 hours for spheres with one month exposure to field conditions (the June cohort).
+After longer exposure to field conditions, \textit{D.
+antiqua} mortality tended to decline over the course of 72 hours.
 
 \paragraph{Field Damage}
+
+Deployment of the attract and kill solution of spinosad containing spheres did not substantially affect end of season onion loss as a result of all mortality factors (Figure \ref{fig:figure4}A), but did influence cumulative damage as a result of \textit{D.
+antiqua} larval feeding (Figure \ref{fig:figure4}B).
+Treatment solution (Insecticide, No Insectide, Spinosad Sphere, Sticky Card) significantly (F = 5.8, df = 3, p = 0.005) explained approximately 38\% of the observed variation in end of season onion stand loss as a result of all mortality factors ($R^2_{adj}$ = 0.38, p = 0.005, Figure \ref{fig:figure4}A).
+The presence of Delia Lure did not significantly (p \textgreater 0.05) affect end of season onion stand loss.
+Insecticide treatment worked best at preventing end of season stand loss (Figure \ref{fig:figure4}A).
+The no insecticide treatment was highly variable and not significantly (p \textgreater 0.05)  different from insecticide controls.
+Spinosad and sticky card treatments were not significantly different from no insecticide treatments, but were significantly worse than insecticide controls.
+
+Cumulative damage as a result of \textit{D.
+antiqua} larval feeding was significantly explained by treatment solution ($\chi^2$ = 42.2, df = 3, p \textless 0.001), the presence of Delia Lure ($\chi^2$ = 10.0, df = 1, p = 0.001), and their interaction ($\chi^2$ = 21.4, df = 1 p \textless 0.001).
+Cumulative damage due to feeding by \textit{D.
+antiqua} larvae over the course of the field season ranged from 0 in some control plots to 82 dead \textit{D.
+antiqua} plants in a few plots.
+This amounts to approximately 20-30\% losses of onion directly attributable feeding by \textit{D.
+antiqua} larvae.
+All treatments were significantly worse than insecticide controls which had very low levels of \textit{D.
+antiqua} damage (Figure \ref{fig:figure4}B).
+Pairing Delia Lure with spinosad containing spheres significantly reduced damage by \textit{D.
+antiqua} larvae by 72$\pm$10\% (p \textless 0.001) compared to spinosad spheres alone.
+Pairing Delia Lure with sticky cards had the opposite effect (Figure \ref{fig:figure4}B).
+
+\paragraph{Enhanced Formulation}
+
+Treatment significantly explained observed \textit{D.
+antiqua} damage in field cage trials with the enhanced formulation ($\chi^2$ = 23.9, df = 2, p \textless 0.001).
+The enhanced formulation (spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different than spinosad-only treatments with 0.5\% spinosad containing spheres.
+Both treatments containing spinosad performed significantly better than the no insecticide controls (p \textless 0.05).
 
@@
 antiqua} mortality in the presence of spinosad treated spheres.
-(A) Raw data of effects of exposure time and spinosad rate on mortality of adult onion maggot flies.
+(A) Raw data of effects of exposure time and spinosad rate on mortality of adult \textit{D.
+antiqua} flies.
 Light points indicate individual observations.
 Solid points and error bars denote mean and 95\% confidence intervals respectively.
-(B) Main effects of spinosad rate on adult onion maggot mortality.
+(B) Main effects of spinosad rate on adult \textit{D.
+antiqua} mortality.
 Points and error bars denote mean effect and 95\% confidence intervals respectively.
 Different letters denote significant differences (p \textless 0.05).
-(C) Main effect of exposure time on adult onion maggot mortality.
+(C) Main effect of exposure time on adult \textit{D.
+antiqua} mortality.
 Line and shaded area denote effect and 95\% confidence region respectively.
@@
 (A) End of season stand loss of onions (number of dead onion plants) as a result of all mortality factors.
-(B) Cumulative damage (number of dead onion plants) as a result of onion maggot larval feeding.
+(B) Cumulative damage (number of dead onion plants) as a result of \textit{D.
+antiqua} larval feeding.
 Light points indicate observed values.
@@
 \caption{Field damage of onion in enclosed cages with differing spinosad sphere formulations.
-Cumulative damage is number of dead plants as a result of onion maggot damage.
+Cumulative damage is number of dead plants as a result of \textit{D.
+antiqua} damage.
 Points and error bars denote mean and 95\% confidence intervals respectively.
@@
 
+Using spinosad containing spheres as an attract and kill solution for control of \textit{D.
+antiqua} populations may be an effective integrated pest management tool.
+Over the course of the three field seasons, with three generations per year (Figure \ref{fig:figure1}), the attract and kill solution was able to consistently inflict mortality on adult \textit{D.
+antiqua} flies, even after prolonged exposure to field conditions (Figure \ref{fig:figure2}).
+While prolonged field exposure did tend to reduce efficacy (Figure \ref{fig:figure2}C) and change the dynamics of mortality (Figure \ref{fig:figure3}), any effects were marginal and may be due to melting of the paraffin solution containing the spinosad (Figure \ref{fig:figure2}D).
+
+Importantly for practical use of this technique, higher doses of spinosad did not have noticeable effects on \textit{D.
+antiqua} mortality.
+The low rate of spinosad containing spheres resulted in adult \textit{D.
+antiqua} mortality that was not significantly different than mortality resulting from contact with spheres containing higher levels of spinosad (Figure \ref{fig:figure2}B).
+This suggests that inclusion of spinosad as the insecticide component of this attract and kill technique was not only an effective choice for implementation of an attract and kill strategy, but also is a viable option even at low doses.
+
+Using \textit{D.
+antiqua} population averages from field experiments and mortality achieved by field-exposed spheres over time assessed in the laboratory, numbers of adult \textit{D.
+antiqua}  killed as a result of the attract and kill strategy can be estimated.
+During peak flights, approximately 272 \textit{D.
+antiqua} adults (both males and females) were caught on average per week.
+Over the course of the field season, approximately 64 adults were caught by sticky cards on average per week.
+Assuming spinosad containing spheres kill approximately 54\% of the adults they contact, over the course of a 16 week season, this attract and kill solution could have killed approximately 553 \textit{D.
+antiqua} adults (16 weeks x 64 adults on average per week * 0.54 mortality) per spinosad containing sphere.
+
+Comparisons of attract and kill strategies with insecticide and no insecticide controls suggest that spinosad containing spheres are controlling some damage by \textit{D.
+antiqua} larvae.
+Spinosad spheres in conjunction with the attractive Delia Lure resulted in levels of damage almost as good as insecticide controls, but with variation that led to overlap with no insecticide negative controls.
+In caged field trials, spinosad containing spheres reduced damage resulting from \textit{D.
+antiqua} feeding to below that of no insecticide controls.
+Interestingly, pairing Delia Lure with sticky cards produced higher levels of damage.
+This is likely because the kill part of the attract and kill sticky card solution was ineffective; Delia Lure likely attracted adult fly populations to plots but sticky cards did not cause sufficient mortality.
+Augmenting spinosad spheres with ammonium carbonate and casein hydrolysate did not appreciably change control with this attract and kill method.
+
+While not as effective as insecticide controls, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
+Spinosad spheres do cause adult \textit{D.
+antiqua} mortality over extended field seasons.
+In situations where immediate reduction in damage from \textit{D.
+antiqua} is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.
+Additionally, this attract and kill approach could be used as a control option where conventional pesticides are no longer effective or available.
+This strategy could also hold promise as an additional mortality factor in longer term management to control \textit{D.
+antiqua} populations.
+
+Efficacy of this attract and kill strategy using spinosad containing spheres to control \textit{D.
+antiqua} could be enhanced through improving trap placement and density.
+\textit{D.
+antiqua} adults are not uniformly distributed in onion fields, but tend to be found in higher numbers along field edges \citep{werling2006spatial}.
+The numbers of the spinosad containing spheres and their placement along edges of commercial onion fields could be adjusted to have a greater impact on increasing fly mortality and reducing maggot damage.
+A higher density of spheres in locations where maggot damage is a problem might have a more appreciable impact on reducing damage.
+Strategic placement of spinosad spheres in areas where populations are highest may further increase efficacy of this technique.
+Additionally, increasing sphere density and temporally targeting the first \textit{D.
+antiqua} generations that cause the most damage may substantially improve efficacy of this technique and warrant further investigation.
+
 \section*{Acknowledgements}
-Suggestions for acknowledgements?
+We appreciate technical assistance by M.
+Hessney and Delia Lure contributions from J.
+Meneley.
+Starker Wright aided in development and construction of spheres.
+The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.
 

### 2019-09-19 analysis/om-spinosad-field-damage_2007.R
updated figures based on author feedback

@@ -49,68 +49,6 @@ field_damage_time <- field_damage %>%
            cumulative_adj = cumulative/initstnd,
            date = as.factor(date))
 
-# Pull out end of season stand numbers
-stand_numbers <- field_damage_time %>% 
-    group_by(treatment, delia_lure, control_type, replication) %>%
-    summarize(starting_stand = first(initstnd),
-              ending_stand = first(finlst)) %>%
-    mutate(loss = starting_stand - ending_stand)
-
-# Model Stand Loss -----------------------
-
-# Basic model for stand loss
-stand_loss_mod <- lm(loss ~ control_type, 
-                     data = stand_numbers)
-model_diagnostics(stand_loss_mod, to_plot = FALSE)
-outlierTest(stand_loss_mod) # Marginal outlier... leave in
-
-# Post hoc analysis based on Tukey's method
-stand_loss_post_hoc <- emmeans(stand_loss_mod, ~ control_type) %>% 
-    CLD(Letters = LETTERS) %>% 
-    data.frame() %>% 
-    mutate(delia_lure = 'Lure')
-
-
-# Stand Loss Figure -----------------
-
-# Plot end of season stand results
-set.seed(72)
-dodge_width = 0.48
-jitter_width = 0.24
-
-stand_loss_figure <- ggplot(stand_numbers, aes(x = control_type, 
-                          y = loss, color = delia_lure)) +
-    geom_point(position = position_jitterdodge(dodge.width = dodge_width,
-                                               jitter.width = jitter_width),
-               alpha = 0.5) + 
-    scale_color_grey() +
-    stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'point',
-                 position = position_dodge(dodge_width)) + 
-    stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'errorbar',
-                 position = position_dodge(dodge_width),
-                 width = dodge_width/2) + 
-    labs(x = 'Treatment',
-         y = 'End of Season Onion Loss') + 
-    geom_text(data = stand_loss_post_hoc, aes(x = control_type,
-                                              y = 250, 
-                                              label = .group),
-              show.legend = FALSE) + 
-    pest_management_science + 
-    theme(legend.position = c(0.75, 0.25),
-          axis.line.x = element_line(size = 0.48, linetype = 'solid', 
-                                     color = 'black'),
[…]

### 2019-09-19 analysis/om-spinosad-field-damage_2008.R

@@ -85,7 +85,5 @@ control_eval_figure <- ggplot(control_evaluation, aes(x = control_type, y = emme
 
 # Save figure
 ggsave(plot = control_eval_figure, 
-       filename = './figures/raw-figures/figure5-control-eval.pdf',
+       filename = './figures/raw-figures/figure4-control-eval.pdf',
        width = 5, height = 3)
-
-

### 2019-09-19 analysis/om-spinosad-field-time-dose.R

@@ -31,6 +31,14 @@ daily_trap_catch <- field_trap_catch %>%
            date = lubridate::mdy(paste(month, day, '2006')),
            catch = catch * 3)
 
+# Averages for mortality calculations
+daily_trap_catch %>% group_by(month, day, sex) %>% 
+    summarize(weekly_mean = mean(catch)) %>% 
+    ungroup() %>% 
+    group_by(sex) %>% 
+    summarize(max = max(weekly_mean),
+              mean = mean(weekly_mean))
+
 # Plot figure -----------------
 
 # Generate figure

### 2019-09-19 analysis/om-spinosad-lab-time-dose.R

@@ -129,6 +129,9 @@ rate_effect_2006 <- emmeans(mortality_mod_2006, ~ rate, type = 'response') %>%
                                       '0.5% Spinosad', 
                                       '1% Spinosad')))
 
+emmeans(mortality_mod_2006, ~ rate, type = 'response') %>% 
+    contrast(method = 'dunnett')
+
 # Plot figure
 figure1b_lab_rate <- ggplot(rate_effect_2006, aes(x = labels, y = emmean)) + 
     geom_point() + 

### 2019-09-19 manuscript/pest-management-science/main.tex
More adjustments based on author feedback.

@@
 The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials.
-Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows on onion each 12 ft long.
+Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long.
 All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i.
 / 100 g seed).
-Seeds were planted in early May and each plot was caged using PVC pipe and screen mesh.
+Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh.
 One hundred fifty \textit{D.
@@
 
-Deployment of the attract and kill solution of spinosad containing spheres did not substantially affect end of season onion loss as a result of all mortality factors (Figure \ref{fig:figure4}A), but did influence cumulative damage as a result of \textit{D.
-antiqua} larval feeding (Figure \ref{fig:figure4}B).
-Treatment solution (Insecticide, No Insectide, Spinosad Sphere, Sticky Card) significantly (F = 5.8, df = 3, p = 0.005) explained approximately 38\% of the observed variation in end of season onion stand loss as a result of all mortality factors ($R^2_{adj}$ = 0.38, p = 0.005, Figure \ref{fig:figure4}A).
-The presence of Delia Lure did not significantly (p \textgreater 0.05) affect end of season onion stand loss.
-Insecticide treatment worked best at preventing end of season stand loss (Figure \ref{fig:figure4}A).
-The no insecticide treatment was highly variable and not significantly (p \textgreater 0.05)  different from insecticide controls.
-Spinosad and sticky card treatments were not significantly different from no insecticide treatments, but were significantly worse than insecticide controls.
-
+Deployment of the attract and kill solution of spinosad containing spheres did influence cumulative onion damage in the field as a result of \textit{D.
+antiqua} larval feeding (Figure \ref{fig:figure4}A).
 Cumulative damage as a result of \textit{D.
@@
 All treatments were significantly worse than insecticide controls which had very low levels of \textit{D.
-antiqua} damage (Figure \ref{fig:figure4}B).
+antiqua} damage (Figure \ref{fig:figure4}A).
 Pairing Delia Lure with spinosad containing spheres significantly reduced damage by \textit{D.
 antiqua} larvae by 72$\pm$10\% (p \textless 0.001) compared to spinosad spheres alone.
-Pairing Delia Lure with sticky cards had the opposite effect (Figure \ref{fig:figure4}B).
+Pairing Delia Lure with sticky cards had the opposite effect (Figure \ref{fig:figure4}A).
 
@@
 antiqua} damage in field cage trials with the enhanced formulation ($\chi^2$ = 23.9, df = 2, p \textless 0.001).
-The enhanced formulation (spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different than spinosad-only treatments with 0.5\% spinosad containing spheres.
-Both treatments containing spinosad performed significantly better than the no insecticide controls (p \textless 0.05).
+The enhanced formulation (spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different than spinosad-only treatments with 0.5\% spinosad containing spheres (Figure \ref{fig:figure4}B).
+Both treatments containing spinosad performed significantly better than the no insecticide controls (p \textless 0.05, Figure \ref{fig:figure4}B).
 
@@
 \caption{Adult onion maggot (\textit{D.
-antiqua} mortality in the presence of spinosad treated spheres.
+antiqua}) mortality in the presence of spinosad treated spheres.
 (A) Raw data of effects of exposure time and spinosad rate on mortality of adult \textit{D.
@@
 \includegraphics[width = 8cm]{figures/final-figures/figure-3.pdf}
-\caption{Adult onion maggot fly mortality following introduction to cages containing spinosad treated spheres.
+\caption{Adult onion maggot (\textit{D.
+antiqua}) fly mortality following introduction to cages containing spinosad treated spheres.
 Spheres were treated with differing rates of spinosad (rows) and exposed to field conditions for increasing amounts of time (column).
@@
 \caption{Field damage of onions.
-(A) End of season stand loss of onions (number of dead onion plants) as a result of all mortality factors.
-(B) Cumulative damage (number of dead onion plants) as a result of \textit{D.
+(A) Cumulative damage (number of dead onion plants) as a result of \textit{D.
 antiqua} larval feeding.
-Light points indicate observed values.
 Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.
 Different letters denote significant differences (p \textless 0.05).
-}
-\label{fig:figure4}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/final-figures/figure-5.pdf}
-\caption{Field damage of onion in enclosed cages with differing spinosad sphere formulations.
+(B) Field damage of onion in enclosed cages with differing spinosad sphere formulations.
 Cumulative damage is number of dead plants as a result of \textit{D.
@@
 }
-\label{fig:figure5}
+\label{fig:figure4}
 \end{figure}

### 2019-10-03 manuscript/pest-management-science/main.tex
more author feedback...

@@
 Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.
-These options may not be viable in organic production systems or areas where insecticide-resistant populations occur.
+These options may not be viable in organic production systems or situations where insecticide-resistant populations occur.
 Here we explore the efficacy of an attract and kill strategy for control of \textit{D.
@@
 Feeding by \textit{D.
-antiqua} larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the produce.
+antiqua} larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the bulb.
 
@@
 antiqua}.
-Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective \textit{D.
+Cultural practices such as crop rotation, removal of damaged cull and volunteer onions, and delayed planting are also effective \textit{D.
 antiqua} management tactics \citep{martinson1988dispersal,finch1985influence,nault2011delaying} but they are not typically adopted by large-scale commercial growers.
@@
 antiqua} control, we elected to use spinosad as the toxicant.
-Spinosad is a naturally derived neurotoxic insecticide originally isolated from the soil-dwelling actinomycete \citep{Saccharopolyspora spinosa} \citep{racke2007reduced}.
+Spinosad is a naturally derived neurotoxic insecticide originally isolated from the soil-dwelling actinomycete \textit{Saccharopolyspora spinosa} \citep{racke2007reduced}.
 It has been approved for use on over 150 fruit and vegetable crops in the United States and is certified for use in organic production by the USDA National Organic Standards Board and Organic Materials Review Institute (OMRI) \citep{racke2007reduced,williams2003naturally}.
 In addition, spinosad has substantially lower non-target effects relative to conventional pesticides and a low residual toxicity \citep{williams2003naturally}.
-Because of its complementary nature to current conventional management of onion maggot and potential use in organic production systems, spinosad was included in the development of an attract and kill solution for \textit{D.
+Because of its complementary nature to current conventional management of \textit{D.
+antiqua} and potential use in organic production systems, spinosad was included in the development of an attract and kill solution for \textit{D.
 antiqua}.
@@
 We hypothesized that these spinosad-attractive spheres would kill \textit{D.
-antiqua} flies and significantly reduce maggot damage to onions.
+antiqua} flies and significantly reduce maggot damage to onions in the field.
 This study was conducted over the course of three field seasons in upstate New York.
@@
 
-During the period these trials were conducted in upstate New York, \textit{Delia antiqua} had three generations (Figure \ref{fig:figure1}).
+During the period these trials were conducted in upstate New York, \textit{D.
+antiqua} had three generations (Figure \ref{fig:figure1}).
 The first population of adults peaked in June, the second in late July, and the third in August.
@@
 
-Comparisons of attract and kill strategies with insecticide and no insecticide controls suggest that spinosad containing spheres are controlling some damage by \textit{D.
+Comparisons of attract and kill strategies with insecticide and no insecticide controls suggest that spinosad containing spheres are reducing some damage by \textit{D.
 antiqua} larvae.
-Spinosad spheres in conjunction with the attractive Delia Lure resulted in levels of damage almost as good as insecticide controls, but with variation that led to overlap with no insecticide negative controls.
+Spinosad spheres in conjunction with the attractive Delia Lure resulted in levels of onion damage almost as good as insecticide controls, but with variation that led to overlap with no insecticide negative controls.
 In caged field trials, spinosad containing spheres reduced damage resulting from \textit{D.
@@
 Additionally, increasing sphere density and temporally targeting the first \textit{D.
-antiqua} generations that cause the most damage may substantially improve efficacy of this technique and warrant further investigation.
+antiqua} generation which causes the most damage, may substantially improve efficacy of this technique and warrant further investigation.
 

### 2019-11-11 manuscript/pest-management-science/main.tex

@@
 
-Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.
+BACKGROUND: Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.
 Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.
@@
 antiqua} and reduce crop losses.
-Spinosad containing spheres were able to consistently kill \textit{D.
+
+RESULTS: Spinosad containing spheres were able to consistently kill \textit{D.
 antiqua} adults over the course of the field season (mortality range: between 49\% and 59\% on average).
-Pairing spinosad spheres with Delia Lure increased efficacy by 72\% compared with the attract and kill strategy alone.
+Pairing spinosad spheres with Delia Lure increased efficacy by 72\% compared with the spheres alone.
 Performance of this attract and kill strategy also can reduce damage by \textit{D.
 antiqua}  larvae in the field, but it did not achieve a level of control comparable to the level provided by a conventional insecticide treatment.
-Implementation of this attract and kill strategy could be a valuable tool in situations where conventional pesticides are either not available or desired, where additional control techniques are needed, or to provide a season-long option for control of \textit{D.
+
+CONCLUSION: Implementation of this attract and kill strategy could be a valuable tool in situations where conventional pesticides are either not available or desired, where additional control techniques are needed, or to provide a season-long option for control of \textit{D.
 antiqua} populations.

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex
template for revision

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{scrextend}
\usepackage{lastpage}
\usepackage{geometry}
 \geometry{
 left = 1.5in,
 right = 1.5in,
 top = 1in
 }
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{\includegraphics[height= 1cm]{ento1.png}\vspace{1em}}
\chead{\includegraphics[width = 5cm]{agritech1.png}}
\lhead{\includegraphics[width=3cm]{acet1.png}}

\fancyfoot{}
\setlength\headheight{40.8pt}
\RequirePackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\fontsize{10}{15}\bfseries}{\thesection}{0em}{}
\titlespacing{\section}{}{1.24em}{0.24em}

\usepackage[default]{lato}
\usepackage[T1]{fontenc}

\cfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\begin{document}

\begin{addmargin}[3.8in]{}
Willett, Filgueiras, \newline
Nyrop and Nault \newline
----------------------------- \newline
Denis S. Willett\newline
Department of Entomology \newline
Cornell AgriTech  \newline
Cornell University \newline
15 Castle Creek Drive \newline
Geneva, NY 14456 \newline
deniswillett@cornell.edu \newline
\end{addmargin}
\setlength{\parindent}{0cm}

December 24, 2019

\vspace{1.24em}

Journal of Applied Entomology

\vspace{1.24em}

Dear Prof. Stefan Vidal,

\vspace{0.48em}
\setlength{\parindent}{1.24cm}

Thank you for your consideration of \textit{“Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping”} for publication in the Journal of Applied Entomology.  We have revised the manuscript in accordance with reviewer recommendations.  A complete and detailed account of the revisions is included below.  The reviewer comments were very helpful, much appreciated, and have resulted in a better manuscript.  In addition to submitting a revised version of the manuscript incorporating the latest changes, we are also submitting production quality images.

\vspace{2em}

Much appreciated, \newline

\vspace{1em}

Denis S. Willett
\vspace{0.48em}

Camila C. Filgueiras
\vspace{0.48em}

Jan P. Nyrop
\vspace{0.48em}

Brian A. Nault
\vspace{0.48em}

\vspace{1.4em}

\hline

\setlength\parindent{0pt}

\subsection*{Reviewer 1}

Well-written paper.  I feel the research is new, important and relevant to the industry.  The methods and statistical analysis are appropriate.  I agree with the reported results; a few of the discussion points seem to go a little too far from the scope of research and are not supported with data or referenced material.

\begin{quote}
    \textit{Thank you for reviewing the paper.  We appreciate your comments and concise summary.  We've adjusted the language in accordance with your suggestions and refined discussion points to not expand beyond the scope of research.  }
\end{quote}

One concern is it appears some of the studies may not have been replicated in space or time.  It is stated trials were conducted in 2005 and 2006 but some studies only have 4-5 raw data points and no reported year effects in Table 1.  Please clarify which studies were replicated in space and time.   Below are comments referenced by line number.

\begin{quote}
    \textit{Thanks for your inquiry.  All trials were replicated in space.  Not all trials had year effects; size trials were replicated across years.  It should be noted that the trials were iterative in the sense that improvement decisions were made and incorporated into subsequent trials.  }
\end{quote}

Line 10-12- Consider revising sentence.  Current cultural management especially altering planting date, field location, and crop rotation depend on monitoring.

\begin{quote}
    \textit{Thanks for suggesting this.  We have included your suggestions in the updated version of the paper.  }
\end{quote}

Line 75-76- Were all studies conducted in 2005 and 2006 or just some trials? Please clarify.

\begin{quote}
    \textit{Thanks for your inquiry - please see comments above.}
\end{quote}

Line 88-90- It would be helpful to know what insecticides were applied to the fields during the monitoring period (Late May to Late June) if information is available?

\begin{quote}
    \textit{Great question - The management program almost identically followed the proposals put forth by Reiners et al., 2019. } 
\end{quote}

Line 106- Why wasn't blue used in the study if other studies indicated it attracted \textit{D. antiqua} flies.

\begin{quote}
    \textit{Excellent question - blue wasn't used in this trial because we simply did not imagine that blue would be an attractive color.  The results suggesting that blue could be attractive were published in 2018 - well after we completed this study.  It should be noted that there could be a trade off with use of blue traps however.  While specificity for onion maggot seems higher on blue traps, overall catch numbers suffer. 
    }
\end{quote}

Line 138- Is it necessary to spell out P-values and R2 values when cited in Table 1 for all result sections.  Recommend either referring to Table 1 and leaving out text.

\begin{quote}
    \textit{Thanks for your suggestion.  We've removed the redundancy and just cited Table 1 in the text.  }
\end{quote}

Line 143- "short cylinders numerically caught "X" more females  then cubes and spheres.

\begin{quote}
    \textit{Excellent suggestion.  We've added this additional information in the text.}
\end{quote}

Line 145- This is probably outside the scope of the study but did the larger trap sizes also correspond to capture of more non-target insects?  Did larger traps require additional support to prevent movement in wind?

\begin{quote}
    \textit{Great questions.  While this is somewhat outside the scope of the paper, larger sizes had more insects, but we did not look into quantifying non-targets.  Larger traps did not require much in the form of additional supports for the wind.  The only challenging part of supporting traps was actually the deer population.  At one of our sites, particularly hungry deer devoured our spheres. Must have been pretty hungry put up with the taste.  }
\end{quote}

Line 185- Again, why wasn't blue tested in the study?

\begin{quote}
    \textit{Excellent question.  See previous response}
\end{quote}

Line 202- change "has reduced"

\begin{quote}
    \textit{Thanks for catching this typo.  We have corrected it in the updated version of the manuscript.}
\end{quote}

Line 210-212- This statement is not supported by data nor referenced materials.  The number of flies captured in all treatments is small.  It seems unlikely the number of captured adults even with several traps per field would reduced the overall population enough to influence maggot damage.  It might be worth citing research investigating insecticide applications targeting adults used in combination with trapping and how they influence onion maggot fly populations and onion maggot damage to provide context to other statements in the final paragraph.

\begin{quote}
    \textit{Good point.  We may have gotten ahead of ourselves in discussing future work and upcoming results.  This will have to wait for the next manuscript.  We have adjusted the language towards the end of the discussion to capture the results of the paper and better rely on current literature support.  }
\end{quote}

\subsection*{Reviewer 2}

The authors report on field tests, using different types of traps (shape, colour, baits) aiming at improving catches of onion flies. While I don’t question the importance of improving a trap design to base control measures on the occurrence of these flies in the onion fields I doubt that the authors would be able to contribute to phenological modelling approaches by using these data. No information is provided on the background populations of onion flies in these fields or the damage levels. The authors state that improved traps create the “opportunity for a different, more environmentally friendly, management method”.  Overall, the discussion section is only marginally developed and there are many additional opportunities to refer and discuss studies on maggot flies, carrot flies, or cabbage flies. The whole section on the Attract & Kill approach is not reflecting the state of the art discussion.

\begin{quote}
    \textit{Thank you for your concise summary and for reviewing the paper.  We appreciate your comments and have endeavored to incorporate your suggestions in the revised manuscript.  We have elaborated upon work on other flies and have removed discussion of the Attract and Kill approach while focusing on its contribution to an integrated pest management approach.  }
\end{quote}

Misc.:
25 correct citations throughout the MS: Nault, Straub….-  not B. A. Nault….

\begin{quote}
    \textit{Thank you for pointing this out.  The citations in the version rendered in Word turned out a bit odd.  The citations are correct in the LaTeX version assembled using the JAE template that will be used for publication. }
\end{quote}

29 would be interesting for the reader to learn details about which compounds are involved

\begin{quote}
    \textit{Thanks for your suggestion.  Details about developing resistance are elaborated upon in the cited papers. }
\end{quote}

37 … generations and plant pathogens

\begin{quote}
    \textit{Thanks for the opportunity to clarify.  This has been updated in the revised version of the paper.  }
\end{quote}

49 give reason why insecticide application is not desired – organic production?

\begin{quote}
    \textit{Excellent suggestion to clarify.  It has been adjusted in the revised version of the manuscript. }
\end{quote}

63 (and 70, 182, 186, 299) is this report accessible to readers? Guess not; thus it should not be cited;

\begin{quote}
    \textit{Thanks for your inquiry.  This report is accessible to readers and the general public; it is not behind a pay wall.  For some reason, Word rendered the formatting wrong.  The LaTeX version with the JAE template has the full information including an accessible url for public perusal.  }
\end{quote}

76 why data from 2005 and 2006; seems a bit outdated!

\begin{quote}
    \textit{Excellent question.  While the trials were conducted in 2005 and 2006, renewed interest in alternative management options for onion maggot in New York has prompted us to put together this paper. We feel this is useful information that serves as a base for future work in the pipeline documenting effective onion maggot management using the trap development documented here.  }
\end{quote}

80ff the layout of the traps within the fields is not sufficiently outlined in detail. The position of the traps was most probably within the fields; however, adjacent fields and the incidence of surrounding onion field may have had an influence on trap catches as well. What about wind direction? Do onion flies have rendezvous-places (at least known from Delia platura)?  What means “long edge of an onion … field”?  
\begin{quote}
    \textit{Thanks for your suggestion.  We have elaborated on trap location to some extent in the text.  GPS coordinates of trap locations are also available upon request.  We did not control for nor record wind direction.  \textit{D. antiqua} does have rendezvous places; catch seems to be higher along edges of fields hence the trap placement.  The onion fields are rectangular with the long edge being the longer of the pairs of sides.  }
\end{quote}

92 Why were traps placed at a distance of 15.2 m? Sounds a bit odd! Has this distance been evaluated for interactions? How did time influence trap catches; seems that the traps were exposed for 4 weeks; any differences in trap dynamics for the different types tested?

\begin{quote}
    \textit{Excellent question.  Because our growers work with standard measurements, 50 feet (the 15.2m equivalent) divides up the field nicely and uniformly.  This distance was additionally chosen because we believe that it is much larger than would cause interactions.  We did not see much variation in trap dynamics over time for the designs tested.  
    }
\end{quote}

152 what is meant with trend? This is not a statistically resilient term – significant or not significant!

\begin{quote}
    \textit{Excellent question.  This is actually a statistical term and there are numerous types of trend analysis.  In linear trend analysis (the case here) trend is essentially slope and can be fitted using the least squares method.  In analysis with sizes, diameter can be treated as either a categorical (the case in our paper) or continuous variable.  In the continuous case, the trend would be the slope of the relationship between size and trap catch and the coefficient of this term in the linear model.  Trends were similar in our studies because as trap sphere diameter increased, trap catch also increased for both males and females.  This is an important applied point because there seems to be little difference between the sexes.  We did not dive further into trend analysis nor pursue the continuous analysis approach because we felt that display of the categorical approach would be more intuitive for management professionals and because identification of the scaling factor for continuity would require further research to disentangle which is more important: diameter, volume, or surface area.  
    }
\end{quote}

204 I doubt that a mass trapping approach would result in control of these flies. Flies may be attracted to these traps from adjacent fields or landscapes, thus high trap catches may not reflect the real population densities. Are data available which clearly demonstrate that increasing catches in one field reduce onion damage?

\begin{quote}
    \textit{Great question.  This point also relates to your inquiry regarding the relevance of publishing data from 2005 and 2006.  More recent work using the results related report on the efficacy of using this approach to reduce onion damage in the field.  }
\end{quote}

Figures: It is a bit strange that the CVs of the males are always much lower than those of the females – this should be discussed. Are females better dispersers? Do the traps attract males or do males seek for females?

\begin{quote}
    \textit{Thanks for your inquiry.  The male catch is always less than females.  We have elaborated upon this in the discussion.  }
\end{quote}

Figures 4: Delia Lure trials have been made 3 times with 4 reps per treatment; however, the figures shows 6 symbols – please explain why 6 and which are solid and shaded points – not visible in the PDF file

\begin{quote}
    \textit{Thanks for mentioning this.  We have clarified in the figure description.  In this case the points are not the raw values (text copied from previous figures), but rather replicate totals.  Your math is correct with the additional consideration that this trial was conducted in two fields bringing the grand total to 3x4x2 = 24.  }
\end{quote}

\end{document}

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex
adding to reviewer revisions

@@
 
-Journal of Applied Entomology
+Pest Management Science
 
@@
 
-Dear Prof. Stefan Vidal,
+Dear Dr. Torto,
 
@@
 
-Thank you for your consideration of \textit{“Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping”} for publication in the Journal of Applied Entomology.
+Thank you for your consideration of \textit{“Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})”} for publication in Pest Management Science.
 We have revised the manuscript in accordance with reviewer recommendations.
@@
 
-\subsection*{Reviewer 1}
+\subsection*{Referee 1}
 
-Well-written paper.
-I feel the research is new, important and relevant to the industry.
-The methods and statistical analysis are appropriate.
-I agree with the reported results; a few of the discussion points seem to go a little too far from the scope of research and are not supported with data or referenced material.
+The authors did a great job writing the manuscript.  The introduction, methods, and results were easy to understand.
 
 \begin{quote}
-    \textit{Thank you for reviewing the paper.
-We appreciate your comments and concise summary.
-We've adjusted the language in accordance with your suggestions and refined discussion points to not expand beyond the scope of research.
+    \textit{Thank you for reading the manuscript and providing constructive feedback.  We appreciate the suggestions and have endeavored to include them in the revised version.  }
+\end{quote}
+
+On lines 54 and 55 the authors state field trials were conducted from 2006 to 2008, but they did NOT describe if all experiments were repeated in 2006, 2007, and 2008.
+The authors need to describe which experiments were conducted each year, how many times each experiment was replicated, and if the experiments were replicated in space and time.
+
+\begin{quote}
+    \textit{Thanks for the opportunity to clarify.
+Details on the timing of trials are now included in at the beginning of each sub-section in the Material and Methods section on lines ....
+In short, the trials were replicated in space and time.
 }
@@
 
-One concern is it appears some of the studies may not have been replicated in space or time.
-It is stated trials were conducted in 2005 and 2006 but some studies only have 4-5 raw data points and no reported year effects in Table 1.
-Please clarify which studies were replicated in space and time.
-Below are comments referenced by line number.
+The authors should add a few sentences describing the field sites (lines 54-56) cropping history (e.g.
+Where onions grown in previous years?) and the reason why the fields were chosen (e.g.
+did the fields have a previous history of onion maggot damage?).
+If experiments were not replicated in space or time it should be noted in the Material and Methods.
 
 \begin{quote}
-    \textit{Thanks for your inquiry.
-All trials were replicated in space.
-Not all trials had year effects; size trials were replicated across years.
-It should be noted that the trials were iterative in the sense that improvement decisions were made and incorporated into subsequent trials.
+    \textit{Thanks for mentioning this opportunity to elaborate.
+Details on cropping history and reasoning behind field site choice have now been included on lines ....
+Information on how experiments were replicated in space and time are also included (see above).
 }
@@
 
-Line 10-12- Consider revising sentence.  Current cultural management especially altering planting date, field location, and crop rotation depend on monitoring.
+In the discussion section the authors made no mention of using spinosad seed treatment as a management option in conventional and organic onion fields.
+Why??
+Spinosad (Regard) seed treatment is currently the primary management method for onion maggot in organic onions, and spinosad is an active ingredient in many conventional seed treatments.
+Spinosad is an active ingredient in the FI500 seed treatment, and Regard alone often provides a similar level of protection compared to FI500.
+Since FI500 resulted in lower maggot damage compared to all "attract and kill" tactics, why would someone recommend attract and kill with spinosad over spinosad seed treatment?
+I strongly recommend the authors discuss the advantages, disadvantages, and compatibility of using spinosad seed treatment and spinosad attract & kill.
+
+The authors should discuss the implications of onion maggot developing resistance to spinosad using the attract and kill tactic.
+e.g.
+Will the attract and kill tactic with spinosad lead to a higher likelihood of onion maggot developing resistance to spinosad?
+This tactic targets egg laying adults, it only provides partial control, and it exposes multiple generations per year to spinosad?
+These factors seem to favor resistance.
+This question is especially relevant as the most popular registered insecticide seed treatments contain spinosad and there are few alternatives in the marketplace.
+
+\subsection*{Referee 2}
+
+The methods and results need some significant improvements.
+I found that methods lacking in details and the analysis not well described.
+I also noted in the annotated file that the quality of the writing in the intro and discussion is markedly different and will need some work to bring them to the same level.
 
 \begin{quote}
-    \textit{Thanks for suggesting this.  We have included your suggestions in the updated version of the paper.  }
-\end{quote}
-
-Line 75-76- Were all studies conducted in 2005 and 2006 or just some trials? Please clarify.
-
-\begin{quote}
-    \textit{Thanks for your inquiry - please see comments above.}
-\end{quote}
-
-Line 88-90- It would be helpful to know what insecticides were applied to the fields during the monitoring period (Late May to Late June) if information is available?
-
-\begin{quote}
-    \textit{Great question - The management program almost identically followed the proposals put forth by Reiners et al., 2019. } 
-\end{quote}
-
-Line 106- Why wasn't blue used in the study if other studies indicated it attracted \textit{D. antiqua} flies.
-
-\begin{quote}
-    \textit{Excellent question - blue wasn't used in this trial because we simply did not imagine that blue would be an attractive color.
-The results suggesting that blue could be attractive were published in 2018 - well after we completed this study.
-It should be noted that there could be a trade off with use of blue traps however.
-While specificity for onion maggot seems higher on blue traps, overall catch numbers suffer.
+    \textit{Thank you for your comments regarding the manuscript.
+We have added extended details to the methods section describing both the field work and analysis.
+Additionally, we have adjusted language in the introduction and discussion.
+We appreciate your feedback in helping improve the manuscript.
 }
@@
 
-Line 138- Is it necessary to spell out P-values and R2 values when cited in Table 1 for all result sections.  Recommend either referring to Table 1 and leaving out text.
+Line 60: Please check and correct.
 
 \begin{quote}
-    \textit{Thanks for your suggestion.  We've removed the redundancy and just cited Table 1 in the text.  }
+    \textit{Thanks for the opportunity to verify this.  It is correct.  'Abut' (spelled exactly that way) means to share a common border. }
 \end{quote}
 
-Line 143- "short cylinders numerically caught "X" more females  then cubes and spheres.
+Line 63: Not sure why its assumed that color and rate are related, explain.
 
 \begin{quote}
-    \textit{Excellent suggestion.  We've added this additional information in the text.}
-\end{quote}
-
-Line 145- This is probably outside the scope of the study but did the larger trap sizes also correspond to capture of more non-target insects?
-Did larger traps require additional support to prevent movement in wind?
-
-\begin{quote}
-    \textit{Great questions.
-While this is somewhat outside the scope of the paper, larger sizes had more insects, but we did not look into quantifying non-targets.
-Larger traps did not require much in the form of additional supports for the wind.
-The only challenging part of supporting traps was actually the deer population.
-At one of our sites, particularly hungry deer devoured our spheres.
-Must have been pretty hungry put up with the taste.
+    \textit{Interesting question.
+There is no assumption that color and rate are related.
+The fact that white spheres are attractive to \textit{D.
+antiqua} is based on previous research in this system.
 }
@@
 
-Line 185- Again, why wasn't blue tested in the study?
+Line 65: Does this sentence belong to the next paragraph? move it there.
 
 \begin{quote}
-    \textit{Excellent question.  See previous response}
+    \textit{Excellent suggestion.  This sentence does seem to be hanging there.  Rather than include it in the subsequent paragraph, we have opted to remove it alltogether.  }
 \end{quote}
 
-Line 202- change "has reduced"
+Line 66: be more specific.
 
 \begin{quote}
-    \textit{Thanks for catching this typo.  We have corrected it in the updated version of the manuscript.}
+    \textit{Thanks for the opportunity to elaborate.  We have included more details as to the timing and location of the trials throughout the methods section, specifically lines .... }
 \end{quote}
 
-Line 210-212- This statement is not supported by data nor referenced materials.
-The number of flies captured in all treatments is small.
-It seems unlikely the number of captured adults even with several traps per field would reduced the overall population enough to influence maggot damage.
-It might be worth citing research investigating insecticide applications targeting adults used in combination with trapping and how they influence onion maggot fly populations and onion maggot damage to provide context to other statements in the final paragraph.
+Line 68: climate or weather?
 
 \begin{quote}
-    \textit{Good point.
-We may have gotten ahead of ourselves in discussing future work and upcoming results.
-This will have to wait for the next manuscript.
-We have adjusted the language towards the end of the discussion to capture the results of the paper and better rely on current literature support.
-}
+    \textit{Interesting question.  We want to use the weather in these trials as a proxy for general exposure to northern climates and have revised the sentence in accordance with your suggestion.  }
 \end{quote}
 
-\subsection*{Reviewer 2}
-
-The authors report on field tests, using different types of traps (shape, colour, baits) aiming at improving catches of onion flies.
-While I don’t question the importance of improving a trap design to base control measures on the occurrence of these flies in the onion fields I doubt that the authors would be able to contribute to phenological modelling approaches by using these data.
-No information is provided on the background populations of onion flies in these fields or the damage levels.
-The authors state that improved traps create the “opportunity for a different, more environmentally friendly, management method”.
-Overall, the discussion section is only marginally developed and there are many additional opportunities to refer and discuss studies on maggot flies, carrot flies, or cabbage flies.
-The whole section on the Attract & Kill approach is not reflecting the state of the art discussion.
+Line 68-69: This was already state above, seems redundant.
 
 \begin{quote}
-    \textit{Thank you for your concise summary and for reviewing the paper.
-We appreciate your comments and have endeavored to incorporate your suggestions in the revised manuscript.
-We have elaborated upon work on other flies and have removed discussion of the Attract and Kill approach while focusing on its contribution to an integrated pest management approach.
-}
+    \textit{Thanks for mentioning this.  We have removed the redundant statement.  }
 \end{quote}
 
-Misc.:
-25 correct citations throughout the MS: Nault, Straub….-  not B. A. Nault….
+Line 71: More details are needed: how many reps/field, how many fields, how much distance between spheres, etc.
+Where in the field relative to the crop were spheres?
+What were they placed on and how high?
 
 \begin{quote}
-    \textit{Thank you for pointing this out.
-The citations in the version rendered in Word turned out a bit odd.
-The citations are correct in the LaTeX version assembled using the JAE template that will be used for publication.
-}
+    \textit{}
 \end{quote}
 
-29 would be interesting for the reader to learn details about which compounds are involved
+Line 77: Which years was this experiment done? Throughout this section pls change to using SI units.
 
-\begin{quote}
-    \textit{Thanks for your suggestion.  Details about developing resistance are elaborated upon in the cited papers. }
-\end{quote}
+Line 91: was this based on a preliminary experiment?
 
-37 … generations and plant pathogens
+Line 99: novel? How was it different from previously used ones?
 
-\begin{quote}
-    \textit{Thanks for the opportunity to clarify.  This has been updated in the revised version of the paper.  }
-\end{quote}
-
-49 give reason why insecticide application is not desired – organic production?
-
-\begin{quote}
-    \textit{Excellent suggestion to clarify.  It has been adjusted in the revised version of the manuscript. }
-\end{quote}
-
-63 (and 70, 182, 186, 299) is this report accessible to readers? Guess not; thus it should not be cited;
-
-\begin{quote}
-    \textit{Thanks for your inquiry.
-This report is accessible to readers and the general public; it is not behind a pay wall.
-For some reason, Word rendered the formatting wrong.
-The LaTeX version with the JAE template has the full information including an accessible url for public perusal.
-}
-\end{quote}
-
-76 why data from 2005 and 2006; seems a bit outdated!
-
-\begin{quote}
-    \textit{Excellent question.
-While the trials were conducted in 2005 and 2006, renewed interest in alternative management options for onion maggot in New York has prompted us to put together this paper.
-We feel this is useful information that serves as a base for future work in the pipeline documenting effective onion maggot management using the trap development documented here.
-}
-\end{quote}
-
-80ff the layout of the traps within the fields is not sufficiently outlined in detail.
-The position of the traps was most probably within the fields; however, adjacent fields and the incidence of surrounding onion field may have had an influence on trap catches as well.
-What about wind direction?
-Do onion flies have rendezvous-places (at least known from Delia platura)?
-What means “long edge of an onion … field”?
-\begin{quote}
-    \textit{Thanks for your suggestion.
-We have elaborated on trap location to some extent in the text.
-GPS coordinates of trap locations are also available upon request.
-We did not control for nor record wind direction.
-\textit{D.
-antiqua} does have rendezvous places; catch seems to be higher along edges of fields hence the trap placement.
-The onion fields are rectangular with the long edge being the longer of the pairs of sides.
-}
-\end{quote}
-
-92 Why were traps placed at a distance of 15.2 m?
-Sounds a bit odd!
-Has this distance been evaluated for interactions?
-How did time influence trap catches; seems that the traps were exposed for 4 weeks; any differences in trap dynamics for the different types tested?
-
-\begin{quote}
-    \textit{Excellent question.
-Because our growers work with standard measurements, 50 feet (the 15.2m equivalent) divides up the field nicely and uniformly.
-This distance was additionally chosen because we believe that it is much larger than would cause interactions.
-We did not see much variation in trap dynamics over time for the designs tested.
-    }
-\end{quote}
-
-152 what is meant with trend? This is not a statistically resilient term – significant or not significant!
-
-\begin{quote}
-    \textit{Excellent question.
-This is actually a statistical term and there are numerous types of trend analysis.
-In linear trend analysis (the case here) trend is essentially slope and can be fitted using the least squares method.
-In analysis with sizes, diameter can be treated as either a categorical (the case in our paper) or continuous variable.
-In the continuous case, the trend would be the slope of the relationship between size and trap catch and the coefficient of this term in the linear model.
-Trends were similar in our studies because as trap sphere diameter increased, trap catch also increased for both males and females.
-This is an important applied point because there seems to be little difference between the sexes.
-We did not dive further into trend analysis nor pursue the continuous analysis approach because we felt that display of the categorical approach would be more intuitive for management professionals and because identification of the scaling factor for continuity would require further research to disentangle which is more important: diameter, volume, or surface area.
-    }
-\end{quote}
-
-204 I doubt that a mass trapping approach would result in control of these flies.
-Flies may be attracted to these traps from adjacent fields or landscapes, thus high trap catches may not reflect the real population densities.
-Are data available which clearly demonstrate that increasing catches in one field reduce onion damage?
-
-\begin{quote}
-    \textit{Great question.
-This point also relates to your inquiry regarding the relevance of publishing data from 2005 and 2006.
-More recent work using the results related report on the efficacy of using this approach to reduce onion damage in the field.
-}
-\end{quote}
-
-Figures: It is a bit strange that the CVs of the males are always much lower than those of the females – this should be discussed.
-Are females better dispersers?
-Do the traps attract males or do males seek for females?
-
-\begin{quote}
-    \textit{Thanks for your inquiry.  The male catch is always less than females.  We have elaborated upon this in the discussion.  }
-\end{quote}
-
-Figures 4: Delia Lure trials have been made 3 times with 4 reps per treatment; however, the figures shows 6 symbols – please explain why 6 and which are solid and shaded points – not visible in the PDF file
-
-\begin{quote}
-    \textit{Thanks for mentioning this.
-We have clarified in the figure description.
-In this case the points are not the raw values (text copied from previous figures), but rather replicate totals.
-Your math is correct with the additional consideration that this trial was conducted in two fields bringing the grand total to 3x4x2 = 24.
-}
-\end{quote}
-
+Line 100: why were these compounds chosen?
 \end{document}

### 2020-01-06 manuscript/pest-management-science/main.tex
prep for revisions
adding to reviewer revisions

@@
 Trials were conducted from May to September.
+All field sites used in these trials had a history of continuous onion production, had historically relatively prominent \textit{D.
+antiqua} populations, and grower collaborators interested in improving management.
 
@@
 Population monitoring of \textit{D.
-antiqua} adults was accomplished by deploying white sticky cards in triplicate along onion field edges in each of six commercial onion fields.
+antiqua} adults was accomplished in 2006 by deploying white sticky cards in triplicate along onion field edges in each of six commercial onion fields.
 Field edges have been identified as ideal locations for trapping adult fly populations, especially when borders abut woodlands \citep{werling2006spatial}.
@@
 To do so, the ability of spinosad spheres to kill \textit{D.
-antiqua} flies was evaluated over the course of multiple field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate climate and dose effects.
-Spheres had three levels of spinosad: No spinosad (Control), 0.5\% spinosad, and 1\% spinosad.
+antiqua} flies was evaluated over the course of 2006 and 2007 field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate weather exposure and dose effects.
 Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively.
@@
 antiqua} larval damage, onions killed or damaged by \textit{D.
-antiqua} larvae were monitored throughout the season.
+antiqua} larvae were monitored throughout the field seasons of 2007 and 2008.
 Onion seed of \textit{Allium cepa} L.
-’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to six treatments in a randomized controlled block design.
+’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.
+Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).
 Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package.
@@
 White sticky cards with and without attractive Delia Lure were also deployed.
-Four replications of each of the six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).
 
-Each individual experimental plot was 8 rows by 30 feet long separated from its nearest neighboring experimental plot by a minimum of 100 feet in any direction.
+Each individual experimental plot was 8 rows by 9.1m  long separated from its nearest neighboring experimental plot by a minimum of 30.5m  in any direction.
 Three weeks following planting, seedlings in the middle two rows were counted to obtain an initial stand count.
@@
 To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate.
-The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials.
+The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008.
 Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long.
@@
 
-\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
+%\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
 

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex
More reviewer comments... :)

@@
 \begin{quote}
-    \textit{}
+    \textit{Thanks for the opportunity to elaborate.  Details about reps, fields, distances, location, and height have been included on lines ....}
 \end{quote}
@@
 
+\begin{quote}
+    \textit{Thanks for the suggestions.
+Information on the timing of the experiment has been added to line....
+Units have also been changed to SI.
+Details have also been added regarding replications and field sites (lines ...).
+}
+\end{quote}
+
 Line 91: was this based on a preliminary experiment?
+
+\begin{quote}
+    \textit{This was indeed based on previous work establishing the attractiveness of the spheres (Willett et al 2019). }
+\end{quote}
 
@@
 
+\begin{quote}
+    \textit{New but not novel.
+It differed from previous formulations with the addition of the two extra components included below.
+We have elaborated on the reasons for developing this on lines.
+}
+\end{quote}
+
 Line 100: why were these compounds chosen?
+
+\begin{quote}
+    \textit{Excellent question.  The thought was that these compounds would help sterilize the paraffin mixture and enhance performance of the spheres over the long term.  }
+\end{quote}
+
+Line 104: was this true for previous experiments as well? If yes, please mention above.
+
+\begin{quote}
+    \textit{This was indeed true for previous experiments as well.  Thanks for the suggestion; these details have been included in the sections above as well.  }
+\end{quote}
+
+Line 108: which years?
+
+\begin{quote}
+    \textit{Great question.  This information has been included and elaborated upon in all methods sections on lines...}
+\end{quote}
+
+Line 110: pls explain how it was analyzed in addition to how it was displayed.
+
+\begin{quote}
+    \textit{Thanks for your inquiry.  It was analyzed using a smoothing function consisting of a generalized additive model with cubic splines.  }
+\end{quote}
+
+Line 112: aren't these the same thing?
+
+\begin{quote}
+    \textit{Thanks for your question.
+Yes and No.
+While linear models and analysis of variance use the same underlying model structure, they have two different objectives and answer two different questions.
+Linear models represent the relationship between independent and dependent variables.
+Analysis of variance compares inter and intra-group variation to examine differences.
+In our case, both approaches were used because we are interested both in modeling relationships and differences between groups.
+}
+\end{quote}
+
+Line 113: I'd like to get more details about which factors you have used, fixed and random.
+
+\begin{quote}
+    \textit{}
+\end{quote}
+
+Line 115: AIC?, BIC? How did you use these to inform model selection? Considerations: third time this word is used in this sentence.
+
+Line 116:  I suggest rewording this sentence. I'm assuming that you are talking about means separation here?
+
+Why use both, why not just one or the other?
+be more explicit about which model goes with what data.
+I'd like to see a list of dependent and independent variables and fixed and random effects.I suggest removing such a blanket statement and being more specific as I mentioned above.
+
+Line 124: need to mention these where you talk about how you built and selected models. These are the tools you used to do that.
+
+Line 128: I'm not following why showing this data is relevant. You also have not done analysis on it. Suggest incorporating it into the rest of the MS effectively.
+
+Line 129: What period was this? Be more specific
+
+Line 130: how were they sexed? Mention in the methods.
+
+Line 131: delete "roughly"
+
+Line 133: What do you mean? Significantly different? Different from what?
+
 \end{document}

### 2020-01-06 manuscript/pest-management-science/main.tex
More reviewer comments... :)

@@
 Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively.
-Deployment in the field followed a randomized controlled block design.
+Deployment in the field followed a randomized controlled block design with six replicates of the 12 treatments (3 spinosad levels x 4 periods of field exposure) across three field sites from 2006 to 2007.
+Spheres were suspended from 30cm long stakes placed along the long side of the onion field at a spacing of 15.2m.
 
@@
 This trial was conducted for both spinosad containing and control spheres.
-Six replications of each of the 12 treatments (3 spinosad levels x 4 periods of field exposure) were conducted.
 
@@
 This treatment was included in the experiment to be a positive control.
-Non-insecticide treated plants were grown from fungicide-only treated seeds and did not receive any attract and kill strategies.
+Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i.
+/ 100 g seed]) and did not receive any attract and kill strategies.
 Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution.
@@
 
-To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate.
+To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate to stabilize the paraffin and improve performance.
 The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008.

### 2020-01-20 manuscript/pest-management-science/reviewer-response/reviewer-response.tex
Updated reviewer responses

@@
 
+\begin{quote}
+    \textit{This is an excellent point.
+We've brought this up and elaborated more on exactly this point in the discussion as well as addressing the advantages and disadvantages of these strategies.
+Thanks for the suggestion.
+Additions can be found on lines ....
+    }
+\end{quote}
+
 The authors should discuss the implications of onion maggot developing resistance to spinosad using the attract and kill tactic.
@@
 This question is especially relevant as the most popular registered insecticide seed treatments contain spinosad and there are few alternatives in the marketplace.
+
+\begin{quote}
+    \textit{Also an excellent suggestion.  This is particularly important in systems where options are rapidly disappearing.  We've addressed this in more detail in the discussion on lines ...
+    }
+\end{quote}
 
@@
 \begin{quote}
-    \textit{}
+    \textit{Thanks for suggesting this inclusion.  We've listed the fixed and random factors used in the analysis on lines ...}
 \end{quote}
@@
 
+\begin{quote}
+    \textit{Good question.
+Both were used to avoid overfitting.
+As both of these criteria penalize likelihood estimates with increasing factors, these were used in consideration with other factors listed to determine best fit models.
+Redundant uses of the word 'considerations' have been removed from the sentence.
+    }
+\end{quote}
+
 Line 116:  I suggest rewording this sentence. I'm assuming that you are talking about means separation here?
 
-Why use both, why not just one or the other?
-be more explicit about which model goes with what data.
+\begin{quote}
+    \textit{Exactly!  We've reworded this sentence to clarify.  Thanks for the suggestion.  }
+\end{quote}
+
+Line 116: Why use both, why not just one or the other?
+
+\begin{quote}
+    \textit{Tukey HSD test generally is used to evaluate all pairwise comparisons.
+Dunnett's test evaluates treatments versus controls.
+In some cases we are only interested in comparisons versus controls (more powerful statistically as the correction for the family wise error rate is lower for less comparisons) while in others we are interested in more detailed comparisons.
+}
+\end{quote}
+
+Line 117: Be more explicit about which model goes with what data.
 I'd like to see a list of dependent and independent variables and fixed and random effects.I suggest removing such a blanket statement and being more specific as I mentioned above.
+
+\begin{quote}
+    \textit{Thanks for the suggestion.
+We've included more detail about the models and factors used for each datasets on lines ...
+In addition, the exact code to run the analysis with annotations and extensive documentation is publicly available on GitHub.
+}
+\end{quote}
 
@@
 
+\begin{quote}
+    \textit{Thanks for the suggestion.
+Given that these tools were used throughout the analysis, we thought it best to consolidate them here rather than repeatedly mentioning them throughout the text.
+}
+\end{quote}
+
 Line 128: I'm not following why showing this data is relevant. You also have not done analysis on it. Suggest incorporating it into the rest of the MS effectively.
+
+\begin{quote}
+    \textit{Thanks for the opportunity to elaborate.
+These data are important as they document three generations in upstate New York.
+This is crucial because it highlights the importance of targeting the first generation to prevent further damage throughout the season.
+While the these data are often mentioned, this figure is important to practitioners in New York state for reference and management decisions.
+Generalized additive models with cubic splines were used to highlight trends in data for management professionals.
+}
+\end{quote}
 
@@
 
-Line 130: how were they sexed? Mention in the methods.
+\begin{quote}
+    \textit{Excellent opportunity to clarify.  Thanks.  We've added details to lines ...}
+\end{quote}
 
@@
 
+\begin{quote}
+    \textit{Excellent suggestion.  'Roughly' has been deleted.  }
+\end{quote}
+
 Line 133: What do you mean? Significantly different? Different from what?
 
+\begin{quote}
+    \textit{Great opportunity to clarify.  This has been explained on lines...}
+\end{quote}
+
+Line 143: Was this peak significantly different from the other times?
+
+\begin{quote}
+    \textit{Interesting question.  While we did not specifically test for this, peaks were either markedly reduced or noticeably absent for subsequent times in Figure 3.  }
+\end{quote}
+
+Line 154: This is compared to what?
+
+\begin{quote}
+    \textit{This comparison was made to spinosad spheres alone - specifics have been addded to lines ...}
+\end{quote}
+
+Line 155: I have a hard time with the letters above bars on this figure. I didn't see the darker colored 'A's. Usually 'A' is used for the highest numbers.
+
+\begin{quote}
+    \textit{Thanks for this suggestion.  We've updated the colors to make this darker.  The lettering scheme was chosen to read alphabetically from left to right.  }
+\end{quote}
+
+Line 155: Was this significant?
+
+\begin{quote}
+    \textit{Great question.  It was indeed significant.  Details have now been included in lines ...}
+\end{quote}
+
+Line 157: be more specific about what treatments.
+
+\begin{quote}
+    \textit{In this case treatment was with the attract and kill strategies.  Details have been added to lines ...}
+\end{quote}
+
+Line 159: are there any F-values or model results to go along with this?
+
+\begin{quote}
+    \textit{Thanks for the opportunity to add more detail.  Additional model statistics have been included on lines ...}
+\end{quote}
+
+\textbf{
+Line 162: The discussion and introduction seems to have been written by different people.
+The language used in the discussion is much more "fuzzy" than in the intro.
+I suggest re-wording much of the discussion to make it less wordy and repetitive and place the findings into a larger context.
+}
+
+Line 167: was this personal observation or speculation?
+
+Line 169: Suggest simplifying this paragraph, its a long and convoluted way of saying that dose didn't matter.
+
 \end{document}

### 2020-01-20 manuscript/pest-management-science/main.tex
Updated reviewer responses

@@
 antiqua} mortality as a result of contact with spheres containing spinosad, linear models and analysis of variance were used.
-Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
-Main effects were teased out from interactions using Tukey and Dunnett post-hoc tests at $P < 0.05$.
+Models were determined after consideration of all factor combinations (rate and exposure time for mortality trials and control strategy and presence of Delia Lure with date as a random effect for field trials) and interactions and selected based on residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria (AIC and BIC), leverage, and likelihood ratio tests.
+Main effects and means separations were evaluated using Tukey and Dunnett post-hoc tests at $P < 0.05$.
 
@@
 
-During the period these trials were conducted in upstate New York, \textit{D.
+Over the course of the 2006 field season when population surveys were conducted in upstate New York, \textit{D.
 antiqua} had three generations (Figure \ref{fig:figure1}).
@@
 
-White spheres containing spinosad caused appreciable mortality of \textit{D.
-antiqua} adults (Figure \ref{fig:figure2}A).
+White spheres containing spinosad caused significant mortality of \textit{D.
+antiqua} adults compared to controls (Figure \ref{fig:figure2}A).
 Both spinosad rate (F =114.3, df=2, p \textless 0.001)  and exposure time (F = 4.7, df = 1, p = 0.03) in the field significantly explained approximately 62\% of the observed variation in adult \textit{D.
@@
 antiqua} larvae by 72$\pm$10\% (p \textless 0.001) compared to spinosad spheres alone.
-Pairing Delia Lure with sticky cards had the opposite effect (Figure \ref{fig:figure4}A).
+Pairing Delia Lure with sticky cards had the opposite effect (P = 0.002, Figure \ref{fig:figure4}A).
 
@@
 
-Treatment significantly explained observed \textit{D.
+Treatment (implementation of attract and kill strategies) significantly explained observed \textit{D.
 antiqua} damage in field cage trials with the enhanced formulation ($\chi^2$ = 23.9, df = 2, p \textless 0.001).
-The enhanced formulation (spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different than spinosad-only treatments with 0.5\% spinosad containing spheres (Figure \ref{fig:figure4}B).
-Both treatments containing spinosad performed significantly better than the no insecticide controls (p \textless 0.05, Figure \ref{fig:figure4}B).
+The enhanced formulation (spinosad +) containing 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate did not perform significantly different (t = -1.9, df = 64, p = 0.13) than spinosad-only treatments with 0.5\% spinosad containing spheres (Figure \ref{fig:figure4}B).
+Both treatments containing spinosad performed significantly better than the no insecticide controls (Spinosad: t = 4.9, df = 64, p \textless 0.0001; Spinosad +: t = 2.9, df = 64, p = 0.01, Figure \ref{fig:figure4}B).
 
@@
 
+The viability of low doses could be particularly important in light of other uses of spinosad in onion fields.
+Spinosad seed treatment is a widespread method used for control of onion maggot and common in other commercial seed treatments \citep{nault2006performance,nault2006onion, wilson2015evaluation}.
+It is also present in the FI500 seed treatment and alone can offer comparable control \citep{nault2006performance,nault2006onion, wilson2015evaluation}.
+These seed treatments are effective options of control of the larval stage; attract and kill methodologies using spinosad evaluated here target the mobile adults.
+While exposure to an additional source of spinosad may foster development of resistance, strategies for preventing development of resistance could include rotating use of the active ingredient for the 'kill' part of the attract and kill strategy.
+
 Using \textit{D.
 antiqua} population averages from field experiments and mortality achieved by field-exposed spheres over time assessed in the laboratory, numbers of adult \textit{D.
-antiqua}  killed as a result of the attract and kill strategy can be estimated.
+antiqua}  killed as a result of the attract and kill strategy using spinosad can be estimated.
 During peak flights, approximately 272 \textit{D.

### 2020-01-21 analysis/2_lab_mortality.R
updated package management

@@ -68,6 +68,7 @@ mortality_mod_2006 <- lm(mortality_rate ~ rate + month,
                     data = mortality_rate_2006)
 model_diagnostics(mortality_mod_2006, to_plot = FALSE)
 
+emmeans(mortality_mod_2006, ~rate + month) %>% contrast()
 
 # Raw data figure ---------------------------
 

### 2020-01-21 analysis/4_field_damage_enhanced.R

@@ -68,6 +68,8 @@ rcompanion::nagelkerke(field_damage_mod, null_damage_mod)
 rmse <- resid(field_damage_mod)^2 %>% mean() %>% sqrt()
 cv_rmse <- rmse/mean(field_damage_time$cumulative)
 
+emmeans(field_damage_mod, ~ control_type) %>% contrast(method = 'pairwise')
+
 # Post hoc contrasts
 control_evaluation <- emmeans(field_damage_mod, ~ control_type) %>% 
     CLD(Letters = LETTERS, 

### 2020-01-21 analysis/1_population_dynamics.R
updated figures with reviewer comments

@@ -13,8 +13,8 @@
 library(tidyverse)
 library(car)
 library(emmeans)
-source('./analysis/model_diagnostics.R')
-source('./analysis/pest_management_science_theme.R')
+source('./analysis/0_model_diagnostics.R')
+source('./analysis/0_pest_management_science_theme.R')
 
 # Load Data ------------------
 field_trap_catch <- read_csv('./data/om-spinosad-field-time-dose-trial-2006.csv', skip = 8)

### 2020-01-21 analysis/2_lab_mortality.R

@@ -14,8 +14,8 @@ library(tidyverse)
 library(car)
 library(emmeans)
 library(ggpubr)
-source('./analysis/model_diagnostics.R')
-source('./analysis/pest_management_science_theme.R')
+source('./analysis/0_model_diagnostics.R')
+source('./analysis/0_pest_management_science_theme.R')
 
 # Load Data ------------------
 
@@ -90,7 +90,7 @@ figure1a_lab_mortality <- ggplot(mortality_rate_2006, aes(x = month, y = mortali
     geom_point(position = position_jitterdodge(dodge.width = dodge_width,
                                                jitter.width = jitter_width),
                alpha = 0.48) + 
-    scale_color_grey() + 
+    scale_color_grey(start = 0.1, end = 0.6) + 
     labs(x = 'Months of Exposure', y = 'Mortality of Onion Maggot Fly Adults') + 
     scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
     theme_bw() + 
@@ -207,7 +207,9 @@ daily_mortality_figure <- ggplot(daily_mortality, aes(x = hours, y = mortality_r
     scale_x_continuous(breaks = c(0,24,48,72)) + 
     labs(y = 'Onion Maggot Mortality Rate',
          x = 'Hours Post Introduction') + 
-    theme_bw() 
+    theme_bw() +
+    theme(panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank())
 
 # Save daily mortality figure
 ggsave(plot = daily_mortality_figure,

### 2020-01-21 analysis/3_field_damage.R

@@ -14,8 +14,8 @@ library(tidyverse)
 library(car)
 library(emmeans)
 library(lme4)
-source('./analysis/model_diagnostics.R')
-source('./analysis/pest_management_science_theme.R')
+source('./analysis/0_model_diagnostics.R')
+source('./analysis/0_pest_management_science_theme.R')
 
 
 # Load data -----------
@@ -103,7 +103,7 @@ cumulative_om_damage_fig <- ggplot(group_differences,
     geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                   position = position_dodge(dodge_width),
                   width = 0.24) + 
-    scale_color_grey() + 
+    scale_color_grey(start = 0.1, end = 0.5) + 
     labs(x = 'Treatment',
          y = 'Cumulative Onion Maggot Damage') + 
     geom_text(aes(y = 44, label = .group),

### 2020-01-21 manuscript/pest-management-science/main.tex
Updates from Overleaf

@@
 antiqua} flies, even after prolonged exposure to field conditions (Figure \ref{fig:figure2}).
-While prolonged field exposure did tend to reduce efficacy (Figure \ref{fig:figure2}C) and change the dynamics of mortality (Figure \ref{fig:figure3}), any effects were marginal and may be due to melting of the paraffin solution containing the spinosad (Figure \ref{fig:figure2}D).
+While prolonged field exposure did tend to reduce efficacy (Figure \ref{fig:figure2}C) and change the dynamics of mortality (Figure \ref{fig:figure3}), any effects were marginal and may be due to melting (personal observation) of the paraffin solution containing the spinosad (Figure \ref{fig:figure2}D).
 
@@
 
-Using \textit{D.
-antiqua} population averages from field experiments and mortality achieved by field-exposed spheres over time assessed in the laboratory, numbers of adult \textit{D.
-antiqua}  killed as a result of the attract and kill strategy using spinosad can be estimated.
+Numbers of adult \textit{D.
+antiqua}  killed as a result of the attract and kill strategy using spinosad can be estimated using \textit{D.
+antiqua} population averages from field experiments and mortality achieved by field-exposed spheres over time assessed in the laboratory.
 During peak flights, approximately 272 \textit{D.
-antiqua} adults (both males and females) were caught on average per week.
+antiqua} adults (both males and females) were caught by sticky cards on average per week.
 Over the course of the field season, approximately 64 adults were caught by sticky cards on average per week.
@@
 This is likely because the kill part of the attract and kill sticky card solution was ineffective; Delia Lure likely attracted adult fly populations to plots but sticky cards did not cause sufficient mortality.
-Augmenting spinosad spheres with ammonium carbonate and casein hydrolysate did not appreciably change control with this attract and kill method.
+Augmenting spinosad spheres with ammonium carbonate and casein hydrolysate, added to increase longevity of the paraffin,  did not appreciably change control with this attract and kill method.
 

### 2020-01-21 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

@@
 
+\begin{quote}
+    \textit{Excellent question.  This was a personal observation. Details to that effect have been included on lines ...}
+\end{quote}
+
 Line 169: Suggest simplifying this paragraph, its a long and convoluted way of saying that dose didn't matter.
 
+\begin{quote}
+    \textit{\textbf{EDIT HERE}}
+\end{quote}
+
+Line 174: Its not clear what this sentence is about, please re-word to clarify.
+
+\begin{quote}
+    \textit{Thanks for the suggestion.  We've reworded the sentence to make it clear that we are estimating numbers of flies killed to place it in the larger context of population management.  }
+\end{quote}
+
+Line 176: caught how and where?
+
+\begin{quote}
+    \textit{Excellent opportunity to clarify.
+This was clarified later in the paragraph, but merits inclusion earlier.
+The adults were caught on sticky traps.
+The phrase has been updated on lines...}
+\end{quote}
+
+Line 180: how does this compare to the many flies that are in a typical onion field? I'm not understanding the value of your analysis. Please clarify and related this info to a larger context.
+
+\begin{quote}
+    \textit{Thanks for your question.
+This directly relates to your inquiry about Figure 1 previously.
+In this paragraph, we place mortality due to the attract and kill strategy in the context of population dynamics in a typical onion field through comparison of data from the population monitoring trial discussed previously.
+}
+\end{quote}
+
+Line 187: Or they were attracted but didn't contact the spheres?
+
+\begin{quote}
+    \textit{Thanks for your inquiry.
+In this case, the discussion is regarding the use of sticky cards.
+The previous part of this phrase explains exactly that the kill part of the strategy with sticky cards was ineffective.
+}
+\end{quote}
+
+Line 188: a bit of discussion on why you suspected that these would change attractiveness would be great.
+
+\begin{quote}
+    \textit{Excellent suggestion.  We've included more details about our rationale on lines ...}
+\end{quote}
+
+Figure 3: suggest removing the background.
+
+\begin{quote}
+    \textit{Thanks for the helpful suggestion.  We've removed the background to enhance visibility.  }
+\end{quote}
+
+Line 196: Feels repetitive, the previous sentence covered this.
+
+\begin{quote}
+    \textit{Thanks for the suggestion.
+These are actually two different cases.
+Resistant populations and organic growers may elect to use this strategy, but have the option to use other methods.
+There are some cases where conventional pesticides to combat onion maggot have been banned or are in the process of becoming banned which would render them unavailable as a control option.
+}
+\end{quote}
+
+Figure 4: light grey is difficult to see, suggest using bars instead of dots and lines.
+
+\begin{quote}
+    \textit{Excellent suggestion.  We've adjusted the color scheme in the figures to enhance readability.  }
+\end{quote}
+
 \end{document}

### 2020-01-21 manuscript/pest-management-science/reviewer-response/reviewer-response.tex
updated with reviewer responses and comments

@@
     \textit{Thanks for the opportunity to clarify.
-Details on the timing of trials are now included in at the beginning of each sub-section in the Material and Methods section on lines ....
+Details on the timing of trials are now included in at the beginning of each sub-section in the Material and Methods section on lines 60-61, 68-69, 73-75, 81-84, and 105-106.
 In short, the trials were replicated in space and time.
@@
     \textit{Thanks for mentioning this opportunity to elaborate.
-Details on cropping history and reasoning behind field site choice have now been included on lines ....
-Information on how experiments were replicated in space and time are also included (see above).
+Details on cropping history and reasoning behind field site choice have now been included on lines 55-58.
+Information on how experiments were replicated in space and time is also included (see above).
 }
@@
 Thanks for the suggestion.
-Additions can be found on lines ....
+Additions can be found on lines 182-188.
     }
@@
 \begin{quote}
-    \textit{Also an excellent suggestion.  This is particularly important in systems where options are rapidly disappearing.  We've addressed this in more detail in the discussion on lines ...
+    \textit{Also an excellent suggestion.  This is particularly important in systems where options are rapidly disappearing.  We've addressed this in more detail in the discussion on lines 186-188.  
     }
@@
 \begin{quote}
-    \textit{Thanks for the opportunity to elaborate.  We have included more details as to the timing and location of the trials throughout the methods section, specifically lines .... }
+    \textit{Thanks for the opportunity to elaborate.
+We have included more details as to the timing and location of the trials throughout the methods section, specifically lines 60-61, 68-69, 73-75, 81-84, and 105-106.
+}
 \end{quote}
@@
 \begin{quote}
-    \textit{Thanks for the opportunity to elaborate.  Details about reps, fields, distances, location, and height have been included on lines ....}
+    \textit{Thanks for the opportunity to elaborate.  Details about reps, fields, distances, location, and height have been included on lines 72-75.
+    }
 \end{quote}
@@
     \textit{Thanks for the suggestions.
-Information on the timing of the experiment has been added to line....
+Information on the timing of the experiment has been added to lines 81-82.
 Units have also been changed to SI.
-Details have also been added regarding replications and field sites (lines ...).
+Details have also been added regarding replications and field sites (lines 83-84).
     }
@@
 It differed from previous formulations with the addition of the two extra components included below.
-We have elaborated on the reasons for developing this on lines.
+We have elaborated on the reasons for developing this on lines 103-104.
     }
@@
 \begin{quote}
-    \textit{Great question.  This information has been included and elaborated upon in all methods sections on lines...}
+    \textit{Great question.  This information has been included and elaborated upon in all methods sections on lines 60-61, 68-69, 73-75, 81-84, and 105-106. 
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{Thanks for suggesting this inclusion.  We've listed the fixed and random factors used in the analysis on lines ...}
+    \textit{Thanks for suggesting this inclusion.  We've listed the fixed and random factors used in the analysis on lines 118-120.
+    }
 \end{quote}
@@
     \textit{Thanks for the suggestion.
-We've included more detail about the models and factors used for each datasets on lines ...
+We've included more detail about the models and factors used for each datasets on lines 118-120.
 In addition, the exact code to run the analysis with annotations and extensive documentation is publicly available on GitHub.
@@
 \begin{quote}
-    \textit{Excellent opportunity to clarify.  Thanks.  We've added details to lines ...}
+    \textit{Excellent opportunity to clarify.  Thanks.  We've added details to line 135.
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{Great opportunity to clarify.  This has been explained on lines...}
+    \textit{Great opportunity to clarify.  This has been explained on line 140.
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{This comparison was made to spinosad spheres alone - specifics have been addded to lines ...}
+    \textit{This comparison was made to spinosad spheres alone - specifics have been addded to lines 161-162.
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{Great question.  It was indeed significant.  Details have now been included in lines ...}
+    \textit{Great question.  It was indeed significant.  Details have now been included in line 162. 
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{In this case treatment was with the attract and kill strategies.  Details have been added to lines ...}
+    \textit{In this case treatment was with the attract and kill strategies.  Details have been added to line 164.  }
 \end{quote}
@@
 \begin{quote}
-    \textit{Thanks for the opportunity to add more detail.  Additional model statistics have been included on lines ...}
+    \textit{Thanks for the opportunity to add more detail.  Additional model statistics have been included on lines 166-167.}
 \end{quote}
 
-\textbf{
 Line 162: The discussion and introduction seems to have been written by different people.
@@
 I suggest re-wording much of the discussion to make it less wordy and repetitive and place the findings into a larger context.
+
+\begin{quote}
+    \textit{Thanks for your suggestions on improving the discussion.  Your comments have made the discussion more clear, direct, and readily accessible to the reader.  
     }
+\end{quote}
 
@@
 \begin{quote}
-    \textit{Excellent question.  This was a personal observation. Details to that effect have been included on lines ...}
+    \textit{Excellent question.  This was a personal observation. Details to that effect have been included on line 175. 
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{\textbf{EDIT HERE}}
+    \textit{Thanks for suggesting this.
+Dose does matter - higher doses are more costly in terms of product used.
+We've endeavored to highlight that higher doses do not seem to significantly augment control.
+}
 \end{quote}
@@
 The adults were caught on sticky traps.
-The phrase has been updated on lines...}
+The phrase has been updated on lines 191-192.
+    }
 \end{quote}
@@
 \begin{quote}
-    \textit{Excellent suggestion.  We've included more details about our rationale on lines ...}
+    \textit{Excellent suggestion.  We've included more details about our rationale on lines 203-204. 
+    }
 \end{quote}

### 2020-01-23 analysis/1_population_dynamics.R
Updated figures with co-author feedback

@@ -46,7 +46,7 @@ population_figure <- ggplot(daily_trap_catch, aes(x = date, y = catch, shape = s
                      color = sex, linetype = sex, fill = sex)) + 
     stat_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) + 
     geom_point(alpha = 0.48) + 
-    scale_color_grey() +
+    scale_color_grey(start = 0.1, end = 0.4) +
     scale_fill_grey() + 
     scale_x_date(expand = c(0,0)) +
     labs(x = '', y = 'Onion Maggot Trap Catch') + 

### 2020-01-23 analysis/2_lab_mortality.R

@@ -123,7 +123,7 @@ ggsave(plot = figure1a_lab_mortality,
 
 # Post-hoc CLD/Tukey examination of marginal means for rate
 rate_effect_2006 <- emmeans(mortality_mod_2006, ~ rate, type = 'response') %>% 
-    CLD(Letters = LETTERS) %>% 
+    CLD(Letters = LETTERS, reversed = TRUE) %>% 
     data.frame() %>% 
     mutate(labels = factor(rate, levels = c('CK', 'LO', 'HI'),
                            labels = c('No Spinosad', 

### 2020-01-23 analysis/3_field_damage.R

@@ -84,7 +84,7 @@ cv_rmse <- rmse/mean(field_damage_time$cumulative)
 
 # Post-hoc
 group_differences <- emmeans(damage_mod, ~ control_type * delia_lure, type = 'response') %>% 
-    CLD(Letters = LETTERS) %>%
+    CLD(Letters = LETTERS, reversed = TRUE) %>%
     mutate(.group = str_trim(.group))
 
 lure_differences <- emmeans(damage_mod, ~ control_type * delia_lure, type = 'response') %>% 
@@ -105,7 +105,7 @@ cumulative_om_damage_fig <- ggplot(group_differences,
                   width = 0.24) + 
     scale_color_grey(start = 0.1, end = 0.5) + 
     labs(x = 'Treatment',
-         y = 'Cumulative Onion Maggot Damage') + 
+         y = 'Cumulative Onion Maggot Damage \n (Number of Dead Plants)') + 
     geom_text(aes(y = 44, label = .group),
               show.legend = FALSE,
               position = position_dodge(dodge_width)) + 

### 2020-01-23 analysis/4_field_damage_enhanced.R

@@ -81,7 +81,7 @@ control_eval_figure <- ggplot(control_evaluation, aes(x = control_type, y = emme
     geom_point() + 
     geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL)) + 
     labs(x = 'Treatment',
-         y = 'Cumulative Onion Maggot Damage') + 
+         y = 'Cumulative Onion Maggot Damage \n (Number of Dead Plants)') + 
     geom_text(aes(label = .group, y = 66)) + 
     pest_management_science
 
@@ -89,3 +89,4 @@ control_eval_figure <- ggplot(control_evaluation, aes(x = control_type, y = emme
 ggsave(plot = control_eval_figure, 
        filename = './figures/raw-figures/figure4-control-eval.pdf',
        width = 5, height = 3)
+

### 2020-01-23 manuscript/pest-management-science/main.tex
updated manuscript with co-author comments

@@
 Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).
-Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package.
+Insecticide-treated plants were grown from seeds treated with the Trigard OMC and Pro-Gro fungicide.
 This treatment was included in the experiment to be a positive control.
@@
 The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008.
-Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long.
+Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m long.
 All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i.
@@
 antiqua} larval feeding.
-Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.
+Solid points and error bars denote mean effects and 95\% confidence intevals respectively.
 Different letters denote significant differences (p \textless 0.05).
@@
 The viability of low doses could be particularly important in light of other uses of spinosad in onion fields.
-Spinosad seed treatment is a widespread method used for control of onion maggot and common in other commercial seed treatments \citep{nault2006performance,nault2006onion, wilson2015evaluation}.
-It is also present in the FI500 seed treatment and alone can offer comparable control \citep{nault2006performance,nault2006onion, wilson2015evaluation}.
+Spinosad is widely used in seed treatments with many growers using the FarMore FI500 seed package which includes spinosad and can independently offer comparable control \citep{nault2006performance,nault2006onion, wilson2015evaluation}.
 These seed treatments are effective options of control of the larval stage; attract and kill methodologies using spinosad evaluated here target the mobile adults.
@@
 
-While not as effective as insecticide controls, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
+While not as effective as insecticide seed treatments, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.
 Spinosad spheres do cause adult \textit{D.

### 2020-03-11 manuscript/pest-management-science/main.tex
Updated references with numbering upon request from Pest Management Science.

@@
 
-\documentclass[alpha-refs]{wiley-article}
+\documentclass[num-refs]{wiley-article}
 % \documentclass[blind,num-refs]{wiley-article}
@@
 Allium crops worldwide suffer attack from onion maggot (\textit{Delia antiqua} Meigen).
-Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \citep{nault2006performance, nault2006onion}.
+Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \cite{nault2006performance, nault2006onion}.
 Other allium crops including garlic (\textit{Allium sativum} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) are similarly susceptible \citep{ellis1979factors,ning2017predicting,nault2007ecology}.
@@
 The lifecycle of \textit{Delia antiqua} plays a large role in its severity as an onion pest.
-In the northern United States, three generations per year are common \citep{eckenrode1975population, hoepting2004insecticide}.
+In the northern United States, three generations per year are common \cite{eckenrode1975population, hoepting2004insecticide}.
 In New York, \textit{D.
@@
 Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).
-Insecticide-treated plants were grown from seeds treated with the Trigard OMC and Pro-Gro fungicide.
+Insecticide-treated plants were grown from seeds treated with Trigard OMC and fungicide.
 This treatment was included in the experiment to be a positive control.
@@
 
-\bibliographystyle{vancouver-authoryear}
+\bibliographystyle{vancouver}
 \bibliography{om-attraction}
